---
title: "Investigate selected samples for further analysis"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
.figure {
    margin-top: 100px;
    margin-bottom: 100px;
}
table {
    margin-top: 10px;
    margin-bottom: 25px !important;
}
th, td { padding: 5px; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(lubridate)
library(gtsummary)
theme_set(theme_classic())
theme_gtsummary_compact()
```

# Overall data selection
## Sample types selection
- collection_site_tissue_type == blood
- sample_type == Buffy Coat, Genomic DNA, MNC, Unprocessed Liquid Tissue

## Patient characteristics
- primary_site_region_desc == "Lymphoma" &  
  histology_desc == "Malignant lymphoma large b-cell diffuse nos"

## Patient clinical data available
- must have height value before first treatment
- must have weight value before first treatment

## Scans data available
- must have a pet/ct scans before first treatment
- OR
- must have a contrast scans before first treatment  
`r emo::ji("spiral_notepad")` *We have pet/ct (without IV contrast) or contrast scans (post contrast). IV contrast affects the density of muscle and possibly fat and mixing between these 2 image types in 1 cohort can be problematic and may cause a paper to be rejected that otherwise would have been accepted.*  
Consequently, I performed 2 patient selections to look at how many patients we could include for each type of scans.

## BMI categories
- *Underweight and normal weight, Overweight, Obese* categories are created following
$$
Underweight and normal weight = bmi < 25
Overweight = bmi ≥ 25 & bmi < 30
Obese = bmi ≥ 30
$$
`r emo::ji("question_mark")`<span style="color:red">**I think you want to have a 2 categories BMI but I am not sure how you would like to group them.**</span>

<br>

# I. Patients with pet/ct scans before treatment
```{r load data petct}
lymphoma_data <- read_rds(paste0(here::here(), "/lymphoma_data_petct_10312023.rds")) %>% 
  mutate_at(c("weight_kg", "bmi", "bmi_cat"), ~ case_when(
           is.na(time_weight_tx_days)      ~ NA,
           TRUE                            ~ .
  )) %>% 
  mutate_at(c("height_m", "bmi", "bmi_cat"), ~ case_when(
           is.na(time_height_tx_days)      ~ NA,
           TRUE                            ~ .
  ))
```
These are some raw data to get an idea of the patients who are included
```{r}
lymphoma_data %>% 
  select(age_at_diagnosis_num, gender_src_desc, 
         race_cr_src_desc_1, ethnicity_src_desc, 
         weight_kg, height_m, 
         bmi, bmi_cat, 
         stage_2018_seer_at_first_contact, 
         stage_tnm_clin_group_2018_cd, 
         stage_tnm_cs_mixed_group_desc) %>% 
  tbl_summary() %>% 
  bold_labels()
```

## 3.Time between pet/ct and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_petct_tx_days))+
  geom_histogram(binwidth = 100, boundary = 0, closed = "left", position = "stack") +
  labs(x="Time from pet/ct to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with pet/ct before treatment",
       subtitle = "Most patients have a scan within 100 days before treatment 
       1 patient has a scan 2013 days before treatment ",
       caption = "Each bar represents 100 days")

lymphoma_data %>%
  select(time_petct_tx_days) %>% 
  tbl_summary() %>% 
  bold_labels()
```

## 4.Time between weight and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_weight_tx_days))+
  geom_histogram(binwidth = 1, boundary = 0, closed = "left") +
  scale_x_continuous(breaks = seq(0, 10, 2))+
  labs(x="Time from weight to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with weight before treatment",
       subtitle = "Most patients have a value within 1 day before treatment",
       caption = "Each bar represents 1 days")

lymphoma_data %>%
  select(time_weight_tx_days) %>% 
  tbl_summary(type = list(time_weight_tx_days ~ "continuous")) %>% 
  bold_labels()
```

## 4.Time between height and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_height_tx_days))+
  geom_histogram(binwidth = 20, boundary = 0, closed = "left") +
  scale_x_continuous(breaks = seq(0, 100, 20))+
  labs(x="Time from height to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with height before treatment",
       subtitle = "Most patients have a value within 20 days before treatment",
       caption = "Each bar represents 20 days")

lymphoma_data %>%
  select(time_height_tx_days) %>% 
  tbl_summary() %>% 
  bold_labels()
```
We lose 3 patients because height date is after treatment. Could we use a value collected after treatment?
```{r, df_print: paged}
lymphoma_data %>%
  filter(is.na(time_height_tx_days)) %>% 
  select(time_height_after_tx_days)
```

## 5. First treatment received
Raw data
```{r}
lymphoma_data %>% 
  select(drug_given_as_part_of_therapy_desc) %>% 
  tbl_summary()
```
<br>

# <span style="color:green">**We have 73 (potentially 76 if we accept later height date) patients with a pet/ct scan before the first treatment.**</span>

<br>

***
<br>

# II. Patients with contrast scans before treatment
```{r load data contrast}
lymphoma_data <- read_rds(paste0(here::here(), "/lymphoma_data_contrast_10312023.rds")) %>% 
  mutate_at(c("weight_kg", "bmi", "bmi_cat"), ~ case_when(
           is.na(time_weight_tx_days)      ~ NA,
           TRUE                            ~ .
  )) %>% 
  mutate_at(c("height_m", "bmi", "bmi_cat"), ~ case_when(
           is.na(time_height_tx_days)      ~ NA,
           TRUE                            ~ .
  ))
```

Same, these are some raw data to get an idea of the patients who are included
```{r}
lymphoma_data %>% 
  select(age_at_diagnosis_num, gender_src_desc, 
         race_cr_src_desc_1, ethnicity_src_desc, 
         weight_kg, height_m, 
         bmi, bmi_cat, 
         stage_2018_seer_at_first_contact,
         stage_tnm_clin_group_2018_cd, 
         stage_tnm_cs_mixed_group_desc) %>% 
  tbl_summary(type = list(age_at_diagnosis_num ~ "continuous")) %>% 
  bold_labels()
```

## 3.Time between contrast and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_contrast_tx_days))+
  geom_histogram(binwidth = 100, boundary = 0, closed = "left", position = "stack") +
  scale_y_continuous(breaks = c(0, 1))+
  labs(x="Time from contrast to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with contrast before treatment",
       caption = "Each bar represents 100 days")

lymphoma_data %>%
  select(time_contrast_tx_days) %>% 
  tbl_summary() %>% 
  bold_labels()
```

## 4.Time between weight and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_weight_tx_days))+
  geom_histogram(binwidth = 1, boundary = 0, closed = "left") +
  scale_x_continuous(breaks = c(0, 1), limits = c(0,1.3))+
  scale_y_continuous(breaks = c(0, 11))+
  labs(x="Time from weight to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with weight before treatment",
       subtitle = "All patients have a value within 1 day before treatment",
       caption = "Each bar represents 1 days")

lymphoma_data %>%
  select(time_weight_tx_days) %>% 
  tbl_summary(type = list(time_weight_tx_days ~ "continuous")) %>% 
  bold_labels()
```

## 4.Time between height and treatment
```{r}
lymphoma_data %>%
  ggplot(aes(x= time_height_tx_days))+
  geom_histogram(binwidth = 20, boundary = 0, closed = "left") +
  scale_x_continuous(breaks = seq(0, 100, 20))+
  labs(x="Time from height to first treatment (in days)", 
       y="Number of Patient",
       title = "Patients with height before treatment",
       subtitle = "Most patients have a value within 20 days before treatment",
       caption = "Each bar represents 20 days")

lymphoma_data %>%
  select(time_height_tx_days) %>% 
  tbl_summary(type = list(time_height_tx_days ~ "continuous")) %>% 
  bold_labels()
```

## 5. First treatment received
Raw data
```{r}
lymphoma_data %>% 
  select(drug_given_as_part_of_therapy_desc) %>% 
  tbl_summary()
```

# <span style="color:green">**We have 11 patients with a contrast scan before the first treatment.**</span>

<br>

***
<br>

`r emo::ji("spiral_notepad")` *For more ideal homogenous cohorts, it is best to stick to either pet/ct or contrast only within 1 cohort.  However, it might be acceptable to combine both if patient numbers are inadequate.*  
Do we want to combine the 2 datasets?


