---
title: "Lymphoma_obesity_analysis"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(gt)
library(survminer)
library(survival)
theme_gtsummary_compact()
theme_set(theme_classic())
```

<style>
div.darkblue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">CH in Lymphoma and obesity analysis</span>

</div>
<br>

```{r load}
lymphoma_data <- read_rds(paste0(here::here(), 
                            "/data/processed data",
                            "/Lymphoma_Data_20251104.rds"))
```

```{r}
lymphoma_data <- lymphoma_data %>% 
  # Index
  mutate(across(c(ends_with("_cm2")
                  ), ~ . / (height_m ^2), 
                .names = "{.col}_index")) %>% 
  # Sarcopenia
  mutate(sarcopenia = case_when(
    sex == "Female" &
      muscle_cm2_index >= 38.5                         ~ "≥ cutoff",
    sex == "Female" &
      muscle_cm2_index < 38.5                          ~ "Sarcopenia",
    sex == "Male" &
      muscle_cm2_index >= 52.4                         ~ "≥ cutoff",
    sex == "Male" &
      muscle_cm2_index < 52.4                          ~ "Sarcopenia"
  )) %>%
  # Myosteatosis - skeletal muscle fat infiltration
  mutate(myosteatosis = case_when(
    bmi < 25 &
      muscle_hu < 41                      ~ "Myosteatosis",
    bmi >= 25 &
      muscle_hu < 33                      ~ "Myosteatosis",
    !is.na(muscle_hu) &
      !is.na(bmi)                         ~ "No myosteatosis"
  )) %>%
  # TAT
  mutate(tat_cm2 = case_when(
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                       ~ NA_real_,
    TRUE                                  ~ vat_cm2 + sat_cm2 + imat_cm2
  )) %>% 
  # V/S ratio
  mutate(v_s_ratio = vat_cm2 / sat_cm2) %>% 
  # Proportion - remove the values if one feature is NA
  mutate(muscle_proportion = muscle_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(vat_proportion = vat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(sat_proportion = sat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(imat_proportion = imat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(across(c(contains("_proportion")), ~ case_when(
    is.na(muscle_cm2) |
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                    ~ NA_real_,
    TRUE                                             ~ .
  )))

lymphoma_data <- lymphoma_data %>% 
  # Make categorical var
  mutate(across(c(ends_with("_index"),
                  "muscle_hu",
                  "vat_cm2", "sat_cm2", "imat_cm2",
                  "tat_cm2",
                  "v_s_ratio",
                  contains("_proportion")
                  ), ~ case_when(
    ntile(., 3) == 1 ~ "Low",
    ntile(., 3) == 2 ~ "Medium",
    ntile(., 3) == 3 ~ "High"),
    .names = "{.col}_tertcat")) %>% 
  mutate(across(c(ends_with("_tertcat")), 
                ~ factor(., levels = 
                           c("Low", "Medium", "High"))))
```

```{r Labeling data}
var_label(lymphoma_data) <- list(age_at_diagnosis_num = "Patient age",
                                 sex = "Sex",
                                 race_cr_src_desc_1	 = "Race (raw)",
                                 race = "Race", ethnicity_src_desc = "Ethnicity",
                                 histology_desc = "Histology",
                                 bmi = "BMI (continuous)",
                                 bmi_cat = "BMI (categorical)",
                                 bsa_du_bois = "BSA (Dubois formula)",
                                 bsa_cat = "BSA (categorical)",
                                 weight_kg = "Weight (kg)",
                                 height_m = "Height (m)",
                                 os_event = "Deaths",
                                 os_time_from_treatment_months = "Follow-up time from treatment (months)",
                                 ch_status = "CH status"
)
```



# I. Patient characteristic by CH status
```{r Patient characteristics}
lymphoma_data %>%
  select(age_at_diagnosis_num,
         sex, 
         race, race_cr_src_desc_1, 
         ethnicity_src_desc,
         # stage_combined,
         histology_desc, 
         survival_time_in_months,
         os_time_from_treatment_months, os_event,
         bmi, bmi_cat, bsa_du_bois, bsa_cat,
         weight_kg, height_m,
         ch_status
         ) %>%
  tbl_summary(by = ch_status) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Patient characteristics**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

# II. Body composition features by BMI
Actual body composition feature don't follow BMI. 
```{r Body composition plot, fig.height=5}
lymphoma_data %>% 
  select(mrn,
         muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu,
         bmi_cat
         ) %>%
  filter(!is.na(bmi_cat)) %>% 
  pivot_longer(-c(mrn, bmi_cat)) %>% 
  ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+
  geom_boxplot()+
  labs(x = "BMI (categories)", y = "Body composition values")+
  scale_color_viridis_d(option = "A", end = c(0.8))+
  theme_classic()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)+
  theme(legend.position = "none")
```

# III. Body composition features by CH status

Most patients (82) have thickness of 3.75 which is often used for Pet/CT so this looks normal. A couple of patient have smaller thickness and 12 have higher thickness value.   
The variables in grey are usually not included in analysis as they don't have meaningful interpretation. I added them here for completeness only.   

<br>

Dan suggested to :   
- Calculate indexed feature (variables need to be divided by height^2).  
- Look at sarcopenia (sarcopenia was defined as muscle indexed [SMI] < 52.4 cm2/m2 for males and SMI < 38.5 cm2/m2 for females).   
- Look at muscle_hu are Hounsfield unit and measure radiodensity. It is important in case of oedema, scaring. It is muscle radiomics, it reflect the muscle quality.    
- Calculate V/S ratio which is VAT divided by SAT.  
- Calculate TAT or total fat tissue (VAT+SAT+IMAT).   
- Calculate tissue proportion (for variable A, we divide variable A by the addition of all the tissue combined muscle+VAT+SAT+IMAT).   

```{r Body composition table}
tbl <- lymphoma_data %>%
  select(muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu, myosteatosis,
         muscle_cm2_index, sarcopenia,
         ends_with("_index"), 
         v_s_ratio, tat_cm2,
         ends_with("_proportion"),
         ends_with("_tertcat"),
         imat_hu, vat_hu, sat_hu,
         muscle_sd, imat_sd, vat_sd,
         sat_sd,
         ch_status
         ) %>%
  tbl_summary(by = ch_status) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

gt_tbl <- tbl |> as_gt(#rownames_to_stub = TRUE
                       )

gt_tbl %>% 
  # data_color(
  #   columns = everything(),
  #   rows = 10:21,
  #   # rows = ends_with("SMI"),
  #   palette = "lightblue", na_color = "lightblue"
  # ) %>%
  # data_color(
  #   columns = everything(),
  #   rows = 24,
  #   # rows = ends_with("SMI"),
  #   palette = "blue", na_color = "blue"
  # ) %>%
  tab_style(
    style = cell_text(color = "lightgrey"),
    locations = cells_body(rows = variable %in% 
                             c("imat_hu", "vat_hu", "sat_hu",
                               "muscle_sd", "imat_sd", "vat_sd",
                               "sat_sd"))
  )
```

I just plotted the original features by CH status. Will update once we figure out the best features to show.
```{r Body composition plot by CH, fig.height=4}
lymphoma_data %>% 
  select(mrn,
         muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu,
         bmi_cat,
         ch_status
         ) %>%
  pivot_longer(-c(mrn, bmi_cat, ch_status)) %>% 
  ggplot(aes(x= ch_status, y= value, color = ch_status))+
  geom_boxplot()+
  labs(x = "CH status", y = "Body composition values")+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme_classic()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)+
  theme(legend.position = "none")
```


# IV. CH and Body composition - glm logistic regression
In the CH table, some feature distributions seems to be different.   
imat_cm2_index, vat_cm2_index (continuous and tertiles)   
v_s_ratio (tertiles only)     
vat_proportion (continuous and tertiles), sat_proportion (continuous and tertiles), imat_proportion (tertiles only)    

I ran the logistic regression with the clinical factor without or with :   
the indexed values;   
the V/S ratio (categorical);   
the tissue proportion variables  (continuous and categorical).   

I am not sure if I always need to include them all for each model (muscle, imat, sat, vat) or if i should just add 1 of the factor...
I will go through the papers to see exactely how they do it.

Also should I do the contrary (predicting VAT for example with CH status as predictor)?
```{r}
glm(ch_status ~
      age_at_diagnosis_num + sex + race,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")

glm(ch_status ~
      age_at_diagnosis_num + sex +
          muscle_cm2_index + vat_cm2_index + sat_cm2_index + imat_cm2_index,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")

glm(ch_status ~
      age_at_diagnosis_num + sex +
          v_s_ratio_tertcat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")

# glm(ch_status ~
#       age_at_diagnosis_num + sex +
#           tat_cm2,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")

glm(ch_status ~
      age_at_diagnosis_num + sex +
          muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")

glm(ch_status ~
      age_at_diagnosis_num + sex +
          muscle_proportion_tertcat + vat_proportion_tertcat + sat_proportion_tertcat + imat_proportion_tertcat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
```

# V. Sensitivity analysis restricted to White patient (to follow when we decide which model to move forward)
```{r}
restric_white_patient <- lymphoma_data %>% 
  filter(race == "White")
```


```{r}
# glm(ch_status ~
#       age_at_diagnosis_num + sex + race,
#     family = "binomial",
#     data = restric_white_patient) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
# 
# glm(ch_status ~
#       age_at_diagnosis_num + sex +
#           muscle_cm2_index + vat_cm2_index + sat_cm2_index + imat_cm2_index,
#     family = "binomial",
#     data = restric_white_patient) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
# 
# glm(ch_status ~
#       age_at_diagnosis_num + sex +
#           muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
#     family = "binomial",
#     data = restric_white_patient) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
```
<br>

# VI. Survival
## Univariable regression analysis
Again in the CH table, some feature distributions seems to be different.   
imat_cm2_index, vat_cm2_index (continuous and tertiles)   
v_s_ratio (tertiles only)     
vat_proportion (continuous and tertiles), sat_proportion (continuous and tertiles), imat_proportion (tertiles only).    
In the univariable analysis, only imat_cm2_index_tertcat show a trend toward a worse survival for the High IMAT tertile group.   
As for the logistic regression, I am not sure here which factor need to be added and will read again the paper sent by Dan.
```{r}
tbl_1 <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("age_at_diagnosis_num",
              "sex", 
              "race", 
              "ch_status",
              "muscle_hu", "myosteatosis",
              "muscle_cm2_index", "imat_cm2_index", "vat_cm2_index", "sat_cm2_index",
              "muscle_cm2_index_tertcat", "imat_cm2_index_tertcat", "vat_cm2_index_tertcat", "sat_cm2_index_tertcat",
              "sarcopenia", "v_s_ratio", "v_s_ratio_tertcat",
              "tat_cm2", "tat_cm2_tertcat",
              "muscle_proportion", "imat_proportion", "vat_proportion", "sat_proportion",
              "muscle_proportion_tertcat", "imat_proportion_tertcat", "vat_proportion_tertcat", "sat_proportion_tertcat",
              "muscle_cm2", "imat_cm2", "vat_cm2", "sat_cm2", 
              "bmi", "bmi_cat")) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
# tbl_1
tbl_2 <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_1, tbl_2), tab_spanner = c("**Univariable**",
                                              "**Multivariable \nClinical only**"))
```


```{r}
# tbl_3 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           muscle_cm2_index + vat_cm2_index + sat_cm2_index + imat_cm2_index,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# tbl_4 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl_merge(list(tbl_3, tbl_4), tab_spanner = c("**Multivariable \nBody Comp \nIndexed**",
#                                               "**Multivariable \nBody Comp \nProportion**"))
# 
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           v_s_ratio_tertcat,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
```

<!-- Additionally adjusted by BMI -->
<!-- ```{r} -->
<!-- coxph(Surv(time = lymphoma_data$os_time_from_treatment_months, -->
<!--              event = lymphoma_data$os_event) ~ age_at_diagnosis_num + -->
<!--           sex + race + ch_status + -->
<!--           muscle_proportion + vat_proportion + sat_proportion + imat_proportion +  -->
<!--         bmi, -->
<!--         data = lymphoma_data)  %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% -->
<!--   bold_p(t = .05) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- ``` -->

## KM by CH
```{r KM PFS 1, fig.height = 7}
ggsurvplot(survfit(Surv(os_time_from_treatment_months, os_event) ~ ch_status,
                   data = lymphoma_data),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (days)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```



