---
title: "Lymphoma_obesity_analysis"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(gt)
library(survminer)
library(survival)
theme_gtsummary_compact()
theme_set(theme_classic())
```

<style>
div.darkblue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">CH in Lymphoma and obesity analysis</span>

</div>
<br>

```{r load}
lymphoma_data <- read_rds(paste0(here::here(), 
                            "/data/processed data",
                            "/Lymphoma_Data_20251104.rds")) %>% 
  select(-ch_status)
path <- fs::path("", "Volumes", "Gillis_Research",
                 "Lab_Data", "LymphomaObesity")
sample_list <- 
  readxl::read_xlsx(paste0(# path,
    here::here(), "/data/raw data",
    "/Lymphoma_Shipping Manifest_EXP2052DNA_PHI_20240504.xlsx"), 
    sheet = "Shipping Manifest_w PHI") %>% 
  janitor::clean_names()
ch_mutation <- 
  readxl::read_xlsx(paste0(# path,
    here::here(), "/data/raw data",
    "/Lymphoma_CHcalls_20260417.xlsx"), 
    na = "NA") %>% 
  janitor::clean_names()
```

```{r}
lymphoma_data <- lymphoma_data %>% 
  mutate(race = factor(race, levels = c("White", "Other"))) %>% 
  mutate(ethnicity_src_desc = na_if(ethnicity_src_desc, "UNKNOWN"))

lymphoma_data <- lymphoma_data %>% 
  # Index
  mutate(across(c(ends_with("_cm2")
                  ), ~ . / (height_m ^2), 
                .names = "{.col}_index")) %>% 
  rename(smi = muscle_cm2_index) %>% 
  # Sarcopenia
  mutate(sarcopenia = case_when(
    sex == "Female" &
      smi >= 38.5                         ~ "≥ cutoff",
    sex == "Female" &
      smi < 38.5                          ~ "Sarcopenia",
    sex == "Male" &
      smi >= 52.4                         ~ "≥ cutoff",
    sex == "Male" &
      smi < 52.4                          ~ "Sarcopenia"
  )) %>%
  # Myosteatosis - skeletal muscle fat infiltration
  mutate(myosteatosis = case_when(
    bmi < 25 &
      muscle_hu < 41                      ~ "Myosteatosis",
    bmi >= 25 &
      muscle_hu < 33                      ~ "Myosteatosis",
    !is.na(muscle_hu) &
      !is.na(bmi)                         ~ "No myosteatosis"
  ), myosteatosis = factor(myosteatosis, levels = c("No myosteatosis", "Myosteatosis"))) %>%
  # TAT
  mutate(tat_cm2 = case_when(
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                       ~ NA_real_,
    TRUE                                  ~ vat_cm2 + sat_cm2 + imat_cm2
  )) %>% 
  mutate(tat_cm2_index = case_when(
    is.na(vat_cm2_index) |
    is.na(sat_cm2_index) |
    is.na(imat_cm2_index)                 ~ NA_real_,
    TRUE                                  ~ vat_cm2_index + sat_cm2_index + imat_cm2_index
  )) %>% 
  # V/S ratio
  mutate(v_s_ratio = vat_cm2 / sat_cm2) %>% 
  mutate(visceral_obesity = case_when(
    v_s_ratio > 0.4                       ~ "Viscerally obese",
    !is.na(v_s_ratio)                     ~ "Not viscerally obese"
  )) %>% 
  # Proportion - remove the values if one feature is NA
  mutate(muscle_proportion = muscle_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(vat_proportion = vat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(sat_proportion = sat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(imat_proportion = imat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  # mutate(muscle_proportionindex = smi / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(vat_proportionindex = vat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(sat_proportionindex = sat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(imat_proportionindex = imat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  mutate(across(c(contains("_proportion")), ~ case_when(
    is.na(muscle_cm2) |
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                    ~ NA_real_,
    TRUE                               ~ .
  )))

lymphoma_data <- lymphoma_data %>% 
  # Make categorical var
  mutate(across(c(smi, ends_with("_index"),
                  "muscle_hu",
                  "vat_cm2", "sat_cm2", "imat_cm2",
                  "tat_cm2",
                  "v_s_ratio",
                  contains("_proportion")
                  ), ~ case_when(
    ntile(., 3) == 1 ~ "Low",
    ntile(., 3) == 2 ~ "Medium",
    ntile(., 3) == 3 ~ "High"),
    .names = "{.col}_tertcat")) %>% 
  mutate(across(c(ends_with("_tertcat")), 
                ~ factor(., levels = 
                           c("Low", "Medium", "High"))))

lymphoma_data <- lymphoma_data %>% 
  # Make 1-standard deviation increase of the feature
  mutate(across(c("muscle_hu", "muscle_cm2",
                  "vat_cm2", "sat_cm2", "imat_cm2",
                  "tat_cm2"#,
                  # contains("_proportion")
                  ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}_sdhr"))

lymphoma_data <- lymphoma_data %>% 
  # Make 1-standard deviation increase of the height indexed feature
  mutate(across(c("smi",
                  "vat_cm2_index", "sat_cm2_index", "imat_cm2_index",
                  "tat_cm2_index"#,
                  # contains("_proportion")
                  ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}sdhr"))

lymphoma_data <- lymphoma_data %>% 
  # Make 1-standard deviation increase of the height indexed feature
  mutate(across(c(contains("_proportion") & where(is.numeric)
                  ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}sdhr"))
```

```{r}
ch_mutation <- ch_mutation %>% 
  inner_join(sample_list %>%
              select(source_sample_id, mrn) %>%
              distinct(), .,
            by = "source_sample_id") %>%
  mutate(mrn = as.character(mrn)) %>%
  mutate(patient_l_ch = case_when(
    l_ch == "TRUE"                     ~ "L-CH"
  )) %>% 
  group_by(mrn) %>%
  mutate(number_of_mutation_per_patient = case_when(
    is.na(gene)                        ~ NA_real_,
    TRUE                               ~ n()
  )) %>% 
  fill(patient_l_ch, .direction = "updown") %>% 
  ungroup()

library(fastDummies)
ch_mutation1 <- ch_mutation %>% 
  filter(!is.na(gene)) %>% 
  select(mrn, number_of_mutation_per_patient, gene, variant_p) %>% 
  unite(mutation_variant, c(gene, variant_p)) %>%
  distinct()

mutation_variant_wide <- dummy_cols(.data = ch_mutation1, select_columns = "mutation_variant",
                                    remove_selected_columns = TRUE,
                                    omit_colname_prefix = FALSE, ignore_na = TRUE) %>%
  group_by(mrn, number_of_mutation_per_patient) %>%
  summarise(across(everything(), sum)) %>%
  ungroup()

ch_mutation1 <- ch_mutation %>% 
  filter(!is.na(gene)) %>% 
  select(mrn, mutation_gene = gene) %>% 
  distinct()

mutation_gene_wide <- dummy_cols(.data = ch_mutation1, select_columns = "mutation_gene",
                                    remove_selected_columns = TRUE,
                                    omit_colname_prefix = FALSE, ignore_na = TRUE) %>%
  group_by(mrn) %>%
  summarise(across(everything(), sum)) %>%
  ungroup()

lymphoma_data <- lymphoma_data %>%
  inner_join(., ch_mutation %>% 
               select(mrn, ch_status, patient_l_ch) %>% 
               distinct(), 
             by = "mrn") %>%
  full_join(., mutation_variant_wide, by = "mrn") %>%
  full_join(., mutation_gene_wide, by = "mrn") %>%
  mutate(across(c(starts_with("mutation_variant") | 
                    starts_with("mutation_gene")
                  ), .fns = ~ replace_na(., 0))) %>% 
  mutate(ch_status = factor(ch_status, levels = c("No CH", "CH")))
```

```{r Labeling data}
var_label(lymphoma_data) <- list(age_at_diagnosis_num = "Patient age",
                                 sex = "Sex",
                                 race_cr_src_desc_1	 = "Race (raw)",
                                 race = "Race", ethnicity_src_desc = "Ethnicity",
                                 histology_desc = "Histology",
                                 bmi = "BMI (kg/m², continuous)",
                                 bmi_cat = "BMI (kg/m², categorical)",
                                 bsa_du_bois = "BSA (Dubois formula)",
                                 bsa_cat = "BSA (categorical)",
                                 weight_kg = "Weight (kg)",
                                 height_m = "Height (m)",
                                 
                                 v_s_ratio = "V/S ratio",
                                 visceral_obesity = "Visceral obesity",
                                 tat_cm2 = "TAT",
                                 smi = "SMI",
                                 sarcopenia = "Sarcopenia",
                                 vat_cm2_index = "VAT (index)",
                                 sat_cm2_index = "SAT (index)",
                                 imat_cm2_index = "IMAT (index)",
                                 tat_cm2_index = "TAT (index)",
                                 muscle_proportion = "Muscle proportion",
                                 vat_proportion = "VAT proportion",
                                 sat_proportion = "SAT proportion",
                                 imat_proportion = "IMAT proportion",
                                 
                                 smisdhr = "SMI",
                                 vat_cm2_indexsdhr = "VAT (index)",
                                 sat_cm2_indexsdhr = "SAT (index)",
                                 imat_cm2_indexsdhr = "IMAT (index)",
                                 tat_cm2_indexsdhr = "TAT (index)",
                                 muscle_proportionsdhr = "Muscle proportion",
                                 vat_proportionsdhr = "VAT proportion",
                                 sat_proportionsdhr = "SAT proportion",
                                 imat_proportionsdhr = "IMAT proportion",
                                 
                                 os_event = "Deaths",
                                 # os_time_from_treatment_months = "Follow-up time from treatment (months)",
                                 ch_status = "CH status"
)
```



# I. Patient characteristic by CH status
```{r Patient characteristics}
lymphoma_data %>%
  select(age_at_diagnosis_num,
         sex, 
         race, race_cr_src_desc_1, 
         ethnicity_src_desc,
         # stage_combined,
         histology_desc, 
         `survival time (months, Registry)` = survival_time_in_months,
         os_time_from_treatment_months, os_event,
         bmi, bmi_cat, bsa_du_bois, bsa_cat,
         weight_kg, height_m,
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(os_time_from_treatment_months ~ 
                                 "{median} [{min}-{max}] ({p25}, {p75})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Patient characteristics**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

# II. BMI, Survival and Body composition
It was described that BMI is not the best predictor for survival. While we would expect patients present in the highest BMI group (≥30) to have the worse survival, they often show a better survival than patient within the middle BMI group (≥25 - <30).
```{r KM OS BMI}
ggsurvplot(survfit(Surv(os_time_from_treatment_months, os_event) ~ bmi_cat,
                   data = lymphoma_data),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,
           palette = c("#000004FF", "#8C2981FF", "#FE9F6DFF"), #"aaas",
           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))

coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ bmi_cat,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_header(label ~ "**Survival association with BMI**")
```

Also, BMI is not the best representation of the actual body composition.   
For example, in our cohort, the highest median value for muscle HU (radiodensity) belong to the patients in the middle BMI category (≥25 - <30).
SAT values are similar between these patients and patients in the high BMI category (≥30).
```{r Body composition plot, fig.height=5}
lymphoma_data %>% 
  select(mrn,
         muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu,
         bmi_cat
         ) %>%
  filter(!is.na(bmi_cat)) %>% 
  pivot_longer(-c(mrn, bmi_cat)) %>% 
  mutate(name = factor(name, levels = c("muscle_hu", "muscle_cm2", 
                                        "vat_cm2", "sat_cm2", "imat_cm2"))) %>% 
  ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+
  geom_boxplot()+
  labs(x = "BMI (categories)", y = "Body composition values")+
  scale_color_viridis_d(option = "A", end = c(0.8))+
  theme_classic()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)+
  theme(legend.position = "none")
```

# III. Body composition features by CH status

Most patients (82) have thickness of 3.75 which is often used for Pet/CT so this looks normal. A couple of patient have smaller thickness and 12 have higher thickness value.   

<br>

Dan suggested to :   
- Calculate indexed feature (variables need to be divided by height^2).  
- Look at sarcopenia (sarcopenia was defined as muscle indexed [SMI] < 52.4 cm2/m2 for males and SMI < 38.5 cm2/m2 for females).   
- Look at muscle_hu are Hounsfield unit and measure radiodensity. It is important in case of oedema, scaring. It is muscle radiomics, it reflect the muscle quality.    
- Calculate V/S ratio which is VAT divided by SAT.  
- Visceral obesity category (visceral obese have a V/S ratio > 0.4).  
- Calculate TAT or total fat tissue (VAT+SAT+IMAT).   
- Calculate tissue proportion (for variable A, we divide variable A by the sum of all the tissue combined muscle+VAT+SAT+IMAT).   
Another thing done in papers is that they used 1-standard deviation increase (z-score) of the feature in the Cox regression model.

<br>

```{r Body composition table}
tbl_raw <- lymphoma_data %>%
  select(muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu, myosteatosis,
         v_s_ratio, visceral_obesity, tat_cm2,
         # ends_with("_tertcat"),
         # imat_hu, vat_hu, sat_hu,
         # muscle_sd, imat_sd, vat_sd,
         # sat_sd,
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} [{sd}] ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_sdhr <- lymphoma_data %>%
#   select(ends_with("_sdhr"), 
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")

tbl_index <- lymphoma_data %>%
  select(smi, sarcopenia,
         vat_cm2_index, sat_cm2_index, imat_cm2_index, tat_cm2_index, 
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} [{sd}] ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_indexsdhr <- lymphoma_data %>%
#   select(ends_with("_indexsdhr"), 
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} [{sd}] ({p25}, {p75})", 
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")

tbl_prop <- lymphoma_data %>%
  select(ends_with("_proportion"),
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} [{sd}] ({min}, {max})", 
                               all_categorical() ~"{n} ({p}%)")) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_propindex <- lymphoma_data %>% # Using height indexed values generate more missing data if height is NA
#   select(ends_with("_proportionindex"),
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} [{sd}] ({min}, {max})",
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>%
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")
```


```{r gt table}
gt_tbl <- tbl_stack(list(tbl_raw, tbl_index, tbl_prop), 
                    group_header = c("Raw features", 
                                     "Indexed features", 
                                     "Tissue proportion")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

I plotted the original features by CH status. Will update once we figure out the best features to show.
```{r Body composition plot by CH, fig.height=4}
lymphoma_data %>% 
  select(mrn,
         muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu,
         bmi_cat,
         ch_status
         ) %>%
  pivot_longer(-c(mrn, bmi_cat, ch_status)) %>% 
  mutate(name = factor(name, levels = c("muscle_hu", "muscle_cm2", 
                                        "vat_cm2", "sat_cm2", "imat_cm2"))) %>% 
  ggplot(aes(x= ch_status, y= value, color = ch_status))+
  geom_boxplot()+
  labs(x = "CH status", y = "Body composition values")+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme_classic()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)+
  theme(legend.position = "none")

lymphoma_data %>% 
  select(mrn,
         ends_with("_proportion"),
         muscle_hu,
         bmi_cat,
         ch_status
         ) %>%
  pivot_longer(-c(mrn, bmi_cat, ch_status)) %>% 
  mutate(name = case_when(
    name == "muscle_hu"                    ~ "Muscle density (HU)", 
    name == "muscle_proportion"            ~ "Muscle proportion",
    name == "vat_proportion"               ~ "VAT proportion", 
    name == "sat_proportion"               ~ "SAT proportion", 
    name == "imat_proportion"              ~ "IMAT proportion"
  )) %>% 
  mutate(name = factor(name, levels = c("Muscle density (HU)", "Muscle proportion",
                                        "VAT proportion", "SAT proportion", 
                                        "IMAT proportion"))) %>%
  ggplot(aes(x= ch_status, y= value, color = ch_status))+
  geom_boxplot()+
  labs(x = NULL, y = "Body composition measure")+
  scale_color_viridis_d(option = "G", end = c(0.8))+
  theme_classic()+
  coord_flip()+
  # facet_grid(cols = vars(name), scales = "free")
  facet_wrap(.~ name, scales = "free", ncol = 2)+
  theme(legend.position = "none")

# ggsave("Figures/Figure S2 Distribution of body composition features by CH status_20260407.jpeg",
#        dpi = 600, units = "in",
#        width = 7,
#        height = 6
#        )
```


# IV. CH and Body composition - glm logistic regression
In the CH table, some feature distributions seems to be different.   
IMAT, VAT for indexed features, and VAT, SAT for abdominal proportion (trend pvalue > 0.05 & < 0.1, only VAT abdominal pvalue < 0.05).

## 1. Regression for association with CH status
### Clinical
```{r CH clinical regression}
glm(ch_status ~
      age_at_diagnosis_num + sex + race + race,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
```

### BMI
https://ashpublications.org/blood/article/144/Supplement%201/872/531065/Mutation-Specific-Differences-in-the-Relationship
In UKBB analyses, we identified genotype-specific patterns of association between BMI and the presence of CH mutations. JAK2 (OR 0.51; 95% CI 0.27-0.96; p=0.036) and DNMT3A mutations (OR 0.92; 95% CI 0.87-0.97; p=0.0028) were negatively associated with a BMI >30 relative to BMI <25, whereas mutations in ASXL1(OR 1.40; 95% CI 1.23-1.60; p=8.8x10-7) and TET2 (OR 1.16; 95% CI 1.04-1.31; p=0.0095) were positively associated with BMI >30.

```{r}
glm(ch_status ~
      age_at_diagnosis_num + sex + race + race + bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      age_at_diagnosis_num + sex + race + race + bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
```

### Association with height-indexed body composition features
Association estimates are reported per 1-SD increase in the body composition metric.   
VAT and IMAT show a trend toward a positive association with the presence of CH mutations.   
Additional adjustment for Age and Sex show similar results.
#### UVA
```{r}
# glm(ch_status ~
#       # age_at_diagnosis_num + sex + race +
#           smi + vat_cm2_index + sat_cm2_index + imat_cm2_index,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_ind <- 
  glm(ch_status ~
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_ind
tbl_ch_vat_ind <- 
  glm(ch_status ~
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_ind
tbl_ch_sat_ind <- 
  glm(ch_status ~
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_ind
tbl_ch_imat_ind <- 
  glm(ch_status ~
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_ind
# glm(ch_status ~
#           v_s_ratio_tertcat,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")

# glm(ch_status ~
#           tat_cm2,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
```

#### MVA
```{r}
tbl_ch_muscle_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_ind_mva
tbl_ch_vat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_ind_mva
tbl_ch_sat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_ind_mva
tbl_ch_imat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_ind_mva
```


### Association with body composition proportion
Association estimates are reported per 1-SD increase in the body composition metric.   
Additional adjustment for Age and Sex exhibit similar results.
#### UVA
```{r}
# glm(ch_status ~
#       # age_at_diagnosis_num + sex + race +
#           muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_prop <- 
  glm(ch_status ~
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_prop
tbl_ch_vat_prop <- 
  glm(ch_status ~
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_prop
tbl_ch_sat_prop <- 
  glm(ch_status ~
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_prop
tbl_ch_imat_prop <- 
  glm(ch_status ~
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_prop
# glm(ch_status ~
#       age_at_diagnosis_num + sex + race +
#           muscle_proportion_tertcat + vat_proportion_tertcat + sat_proportion_tertcat + imat_proportion_tertcat,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE,
#                  intercept = TRUE) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
```

#### MVA
```{r}
tbl_ch_muscle_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_prop_mva
tbl_ch_vat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_prop_mva
tbl_ch_sat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_prop_mva
tbl_ch_imat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + race +
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_prop_mva
```

## 2. Regression for association with CH gene mutations
### a. Count table
```{r}
lymphoma_data %>%
  select(number_of_mutation_per_patient, starts_with("mutation_gene")) %>%
  `colnames<-`(str_remove_all(colnames(.), "mutation_gene_")) %>% 
  tbl_summary() %>%
  bold_labels() %>% 
  modify_header(label ~ "**CH mutations**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

### b. BMI
#### UVA
```{r}
glm(mutation_gene_DNMT3A ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_DNMT3A ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_PPM1D ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_PPM1D ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_TET2 ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
glm(mutation_gene_TET2 ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
```

#### MVA
```{r}
glm(mutation_gene_DNMT3A ~ age_at_diagnosis_num + sex + race +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_DNMT3A ~ age_at_diagnosis_num + sex + race +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_PPM1D ~ age_at_diagnosis_num + sex + race +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_PPM1D ~ age_at_diagnosis_num + sex + race +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_TET2 ~ age_at_diagnosis_num + sex + race +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
glm(mutation_gene_TET2 ~ age_at_diagnosis_num + sex + race +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
```

### c. Association with height-indexed body composition features
Association estimates are reported per 1-SD increase in the body composition metric.   
Mutations in DNMT3A (OR 1.59) seem to be positively associated with higher VAT.
#### UVA
```{r}
tbl_dnmt3a_muscle <- glm(mutation_gene_DNMT3A ~
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat <- glm(mutation_gene_DNMT3A ~
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_sat <- glm(mutation_gene_DNMT3A ~
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_imat <- glm(mutation_gene_DNMT3A ~
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_ppm1d_muscle <- glm(mutation_gene_PPM1D ~
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat <- glm(mutation_gene_PPM1D ~
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_sat <- glm(mutation_gene_PPM1D ~
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_imat <- glm(mutation_gene_PPM1D ~
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_tet2_muscle <- glm(mutation_gene_TET2 ~
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat <- glm(mutation_gene_TET2 ~
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_sat <- glm(mutation_gene_TET2 ~
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_imat <- glm(mutation_gene_TET2 ~
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_muscle <- tbl_merge(list(tbl_dnmt3a_muscle, tbl_ppm1d_muscle, tbl_tet2_muscle), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat <- tbl_merge(list(tbl_dnmt3a_vat, tbl_ppm1d_vat, tbl_tet2_vat))
tbl_sat <- tbl_merge(list(tbl_dnmt3a_sat, tbl_ppm1d_sat, tbl_tet2_sat))
tbl_imat <- tbl_merge(list(tbl_dnmt3a_imat, tbl_ppm1d_imat, tbl_tet2_imat))

gt_tbl <- tbl_stack(list(tbl_muscle, tbl_vat, tbl_sat, tbl_imat), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```


```{r forest plot uva OR inex}
forest_uva_ind <- 
  tbl_dnmt3a_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SMI")) %>%
  mutate(model = "SM") %>% mutate(Pred = "DNMT3A") %>% 
  
  bind_rows(., tbl_dnmt3a_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT (index)")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT (index)")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT (index)")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_ppm1d_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SMI")) %>%
  mutate(model = "SM") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT (index)")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT (index)")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT (index)")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_tet2_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SMI")) %>%
  mutate(model = "SM") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT (index)")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT (index)")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT (index)")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "TET2")) %>% 

  bind_rows(., tbl_ch_muscle_ind %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SMI")) %>%
  mutate(model = "SM") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_vat_ind %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT (index)")) %>%
  mutate(model = "VAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_sat_ind %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT (index)")) %>%
  mutate(model = "SAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_imat_ind %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT (index)")) %>%
  mutate(model = "IMAT") %>%  mutate(Pred = "CH")) %>% 
  
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>% 
  mutate(Characteristic = factor(Characteristic, levels = c("IMAT", "VAT", 
                                                            "SAT", "SMI")))

forest_uva_ind <-
  forest_uva_ind %>% 
  ggplot(aes(y=Characteristic, x=OR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  # theme(text = element_text(size = 15),
  #       axis.title.y = element_blank())
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ Pred, nrow = 1,
             scales = "free",
             strip.position = "top")
forest_uva_ind
# ggsave("Figures/Figure 2A Forest plot MVA OR model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 10,
#        height = 3, compression = "lzw"
#        )
```

#### MVA
```{r}
tbl_dnmt3a_muscle <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_sat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_imat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_ppm1d_muscle <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_sat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_imat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_tet2_muscle <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          smisdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          vat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_sat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          sat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_imat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          imat_cm2_indexsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_muscle <- tbl_merge(list(tbl_dnmt3a_muscle, tbl_ppm1d_muscle, tbl_tet2_muscle), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat <- tbl_merge(list(tbl_dnmt3a_vat, tbl_ppm1d_vat, tbl_tet2_vat))
tbl_sat <- tbl_merge(list(tbl_dnmt3a_sat, tbl_ppm1d_sat, tbl_tet2_sat))
tbl_imat <- tbl_merge(list(tbl_dnmt3a_imat, tbl_ppm1d_imat, tbl_tet2_imat))

gt_tbl <- tbl_stack(list(tbl_muscle, tbl_vat, tbl_sat, tbl_imat), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

### d. Association with body composition proportion
Association estimates are reported per 1-SD increase in the body composition metric.   
#### UVA
```{r}
tbl_dnmt3a_muscle <- glm(mutation_gene_DNMT3A ~
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat <- glm(mutation_gene_DNMT3A ~
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_sat <- glm(mutation_gene_DNMT3A ~
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_imat <- glm(mutation_gene_DNMT3A ~
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_ppm1d_muscle <- glm(mutation_gene_PPM1D ~
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat <- glm(mutation_gene_PPM1D ~
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_sat <- glm(mutation_gene_PPM1D ~
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_imat <- glm(mutation_gene_PPM1D ~
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_tet2_muscle <- glm(mutation_gene_TET2 ~
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat <- glm(mutation_gene_TET2 ~
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_sat <- glm(mutation_gene_TET2 ~
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_imat <- glm(mutation_gene_TET2 ~
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_muscle <- tbl_merge(list(tbl_dnmt3a_muscle, tbl_ppm1d_muscle, tbl_tet2_muscle), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat <- tbl_merge(list(tbl_dnmt3a_vat, tbl_ppm1d_vat, tbl_tet2_vat))
tbl_sat <- tbl_merge(list(tbl_dnmt3a_sat, tbl_ppm1d_sat, tbl_tet2_sat))
tbl_imat <- tbl_merge(list(tbl_dnmt3a_imat, tbl_ppm1d_imat, tbl_tet2_imat))

gt_tbl <- tbl_stack(list(tbl_muscle, tbl_vat, tbl_sat, tbl_imat), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

```{r forest plot uva OR proportion}
forest_uva_prop <- 
  tbl_dnmt3a_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("Muscle proportion")) %>%
  mutate(model = "SM") %>% mutate(Pred = "DNMT3A") %>% 
  
  bind_rows(., tbl_dnmt3a_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT proportion")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT proportion")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT proportion")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_ppm1d_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("Muscle proportion")) %>%
  mutate(model = "SM") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT proportion")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT proportion")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT proportion")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_tet2_muscle %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("Muscle proportion")) %>%
  mutate(model = "SM") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_vat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT proportion")) %>%
  mutate(model = "VAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_sat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT proportion")) %>%
  mutate(model = "SAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_imat %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT proportion")) %>%
  mutate(model = "IMAT") %>% mutate(Pred = "TET2")) %>% 

  bind_rows(., tbl_ch_muscle_prop %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("Muscle proportion")) %>%
  mutate(model = "SM") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_vat_prop %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("VAT proportion")) %>%
  mutate(model = "VAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_sat_prop %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SAT proportion")) %>%
  mutate(model = "SAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_imat_prop %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("IMAT proportion")) %>%
  mutate(model = "IMAT") %>%  mutate(Pred = "CH")) %>% 
  
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>% 
  mutate(Characteristic = factor(Characteristic, levels = c("IMAT", "VAT", 
                                                            "SAT", "Muscle")))

forest_uva_prop <-
  forest_uva_prop %>% 
  ggplot(aes(y=Characteristic, x=OR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  # theme(text = element_text(size = 15),
  #       axis.title.y = element_blank())
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ Pred, nrow = 1,
             scales = "free",
             strip.position = "top")
forest_uva_prop
# ggsave("Figures/Figure 2B Forest plot MVA OR model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 10,
#        height = 3, compression = "lzw"
#        )
```

#### MVA
```{r}
tbl_dnmt3a_muscle <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_sat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_dnmt3a_imat <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + race +
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_ppm1d_muscle <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_sat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_ppm1d_imat <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + race +
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_tet2_muscle <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          muscle_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          vat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_sat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          sat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()
tbl_tet2_imat <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + race +
          imat_proportionsdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE,
                 intercept = TRUE) %>%
  bold_p()

tbl_muscle <- tbl_merge(list(tbl_dnmt3a_muscle, tbl_ppm1d_muscle, tbl_tet2_muscle), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat <- tbl_merge(list(tbl_dnmt3a_vat, tbl_ppm1d_vat, tbl_tet2_vat))
tbl_sat <- tbl_merge(list(tbl_dnmt3a_sat, tbl_ppm1d_sat, tbl_tet2_sat))
tbl_imat <- tbl_merge(list(tbl_dnmt3a_imat, tbl_ppm1d_imat, tbl_tet2_imat))

gt_tbl <- tbl_stack(list(tbl_muscle, tbl_vat, tbl_sat, tbl_imat), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

## 3. Regression for association with CH variants mutations
### Count table - Ns are too snmall to do further regression
```{r}
lymphoma_data %>%
  select(starts_with("mutation_variant")) %>%
  `colnames<-`(str_remove_all(colnames(.), "mutation_variant_")) %>% 
  tbl_summary() %>%
  bold_labels() %>% 
  modify_header(label ~ "**CH mutations**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

# V. Sensitivity analysis restricted to White patient (to follow when we decide which model to move forward)
```{r}
restric_white_patient <- lymphoma_data %>% 
  filter(race == "White")
```



<br>

# VI. Survival
## Univariable regression analysis
Association estimates are reported per 1-SD increase in the body composition metric.

## Univariable
```{r HR uva cox clinical}
tbl_main_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("age_at_diagnosis_num",
              "sex",
              "race",
              "ch_status",
              "bmi", "bmi_cat")) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
# tbl_main_surv
```



```{r HR uva cox BC}
# tbl_raw <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("imat_cm2", "vat_cm2", "sat_cm2",
#               "muscle_hu", "myosteatosis",
#               "v_s_ratio", "tat_cm2"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()

# tbl_sdhr <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("vat_cm2_sdhr", "sat_cm2_sdhr", "imat_cm2_sdhr"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()

# tbl_index <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("smi", "sarcopenia",
#               "imat_cm2_index", "vat_cm2_index", "sat_cm2_index"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
tbl_indexsdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("smisdhr",
              "sarcopenia", 
              "muscle_hu_sdhr", "myosteatosis",
              "vat_cm2_indexsdhr", "sat_cm2_indexsdhr",
              "imat_cm2_indexsdhr", "tat_cm2_indexsdhr",
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

# tbl_prop <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("muscle_proportion", "imat_proportion", "vat_proportion", "sat_proportion"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
tbl_propsdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("muscle_proportionsdhr", "vat_proportionsdhr", "sat_proportionsdhr", "imat_proportionsdhr"
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

# tbl_cat <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("smi_tertcat", "imat_cm2_index_tertcat", "vat_cm2_index_tertcat", "sat_cm2_index_tertcat",
#               "v_s_ratio_tertcat", "tat_cm2_tertcat",
#               "muscle_proportion_tertcat", "imat_proportion_tertcat", "vat_proportion_tertcat", "sat_proportion_tertcat")) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()

```

```{r gt table uva}
gt_tbl <- tbl_stack(list(tbl_main_surv, tbl_indexsdhr_surv, tbl_propsdhr_surv), 
                    group_header = c("Clinical", 
                                     "1-SD normalized Indexed features",
                                     "1-SD normalized Tissue proportion")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```


## Multivariable
## MVA BMI
```{r HR mva bmi}
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + bmi,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_table_styling(
    columns = estimate,
    rows = reference_row %in% TRUE,
    missing_symbol = "Reference"
  ) %>%
  modify_column_merge(
    pattern = "{stat_n} ({stat_nevent})",
    rows = !is.na(stat_nevent)
  ) %>%
  modify_header(stat_n = "**N (Event N)**") %>% 
  # merge all info
  modify_column_merge(
    pattern = "{estimate} ({conf.low}-{conf.high}; p={p.value})",
    rows = !is.na(estimate)
  ) %>%
  remove_abbreviation()

coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + bmi_cat,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_table_styling(
    columns = estimate,
    rows = reference_row %in% TRUE,
    missing_symbol = "Reference"
  ) %>%
  modify_column_merge(
    pattern = "{stat_n} ({stat_nevent})",
    rows = !is.na(stat_nevent)
  ) %>%
  modify_header(stat_n = "**N (Event N)**") %>% 
  # merge all info
  modify_column_merge(
    pattern = "{estimate} ({conf.low}-{conf.high}; p={p.value})",
    rows = !is.na(estimate)
  ) %>%
  remove_abbreviation()
```

```{r}
tbl_1_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_header(label ~ "**MVA Indexed**")
tbl_muscle_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + smisdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_sat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + sat_cm2_indexsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + vat_cm2_indexsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + imat_cm2_indexsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + smisdhr + 
          sat_cm2_indexsdhr +
          vat_cm2_indexsdhr + imat_cm2_indexsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_1_surv, tbl_muscle_ind_surv, tbl_sat_ind_surv, tbl_vat_ind_surv,
               tbl_imat_ind_surv, tbl_all_ind_surv),
          tab_spanner = c("**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metrics**"
                          ))
```
<br>

```{r}
tbl_1_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>% 
  modify_header(label ~ "**MVA Proportion**")
tbl_muscle_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + muscle_proportionsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_sat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + sat_proportionsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + vat_proportionsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + imat_proportionsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + 
          sat_proportionsdhr +
          vat_proportionsdhr + imat_proportionsdhr + muscle_proportionsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_1_surv, tbl_muscle_prop_surv, tbl_sat_prop_surv, tbl_vat_prop_surv,
               tbl_imat_prop_surv, tbl_all_prop_surv),
          tab_spanner = c("**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metric**"
                          ))
```
<br>

## Forest plot
```{r forest plot mva HR index}
forest_mva_ind_surv <- 
  tbl_muscle_ind_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","SMI")) %>%
  mutate(model = "SMI") %>% 
  
  bind_rows(., tbl_sat_ind_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","SAT (index)")) %>%
  mutate(model = "SAT")) %>% 
  
  bind_rows(., tbl_vat_ind_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","VAT (index)")) %>%
  mutate(model = "VAT")) %>% 
  
  bind_rows(., tbl_imat_ind_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","IMAT (index)")) %>%
  mutate(model = "IMAT")) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>% 
  mutate(model = factor(model, levels = c("SMI", "SAT",
                                          "VAT", "IMAT")))

forest_mva_ind_surv <- forest_mva_ind_surv %>% 
  ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  # theme(text = element_text(size = 15),
  #       axis.title.y = element_blank())
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ model, ncol = 1,
             scales = "free",
             strip.position = "right")
forest_mva_ind_surv
# ggsave("Figures/Figure 1A Forest plot MVA index BC model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 4,
#        height = 5, compression = "lzw"
#        )
```

```{r forest plot mva HR proportion}
forest_mva_prop_surv <- 
  tbl_muscle_prop_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","Muscle proportion")) %>%
  mutate(model = "SMI") %>% 
  
  bind_rows(., tbl_sat_prop_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","SAT proportion")) %>%
  mutate(model = "SAT")) %>% 
  
  bind_rows(., tbl_vat_prop_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","VAT proportion")) %>%
  mutate(model = "VAT")) %>% 
  
  bind_rows(., tbl_imat_prop_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","IMAT proportion")) %>%
  mutate(model = "IMAT")) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>% 
  mutate(model = factor(model, levels = c("SMI", "SAT",
                                          "VAT", "IMAT")))

forest_mva_prop_surv <- forest_mva_prop_surv %>% 
  ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ model, ncol = 1,
             scales = "free",
             strip.position = "right")
forest_mva_prop_surv
# ggsave("Figures/Figure 1B Forest plot MVA prop BC model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 4,
#        height = 5, compression = "lzw"
#        )
```


```{r}
forest_prop_surv <- 
  tbl_all_prop_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH","SAT proportion",
                               "VAT proportion",
                               "IMAT proportion") ) %>% 
  mutate(Characteristic = factor(Characteristic, 
                                 levels = c("IMAT proportion",
                                            "VAT proportion",
                                            "SAT proportion","CH"
                                 ))) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  
  mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) #%>% 
  # mutate(name= case_when(
  #   Characteristic == "High marrow burden (≥50%)"      ~ "High marrow \nburden (≥50%)",
  #   Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia \nat Day -5",
  #   Characteristic == "Steroid Use"      ~ "Steroid use",
  #   Characteristic == "Number of prior lines of therapy"      ~ "Number of prior \nlines of therapy",
  #   Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin"
  # ))

forest_prop_surv_fig <- forest_prop_surv %>% 
  ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")
forest_prop_surv_fig

# ggsave("Figures/Figure 1D Forest plot MVA proportion full model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 6,
#        height = 5, compression = "lzw"
#        )

forest_ind_surv <- 
  tbl_all_ind_surv %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("CH", "SMI", "SAT (index)",
                               "VAT (index)",
                               "IMAT (index)") ) %>% 
  mutate(Characteristic = factor(Characteristic, 
                                 levels = c("IMAT (index)",
                                            "VAT (index)",
                                            "SAT (index)",
                                            "SMI", "CH"
                                 ))) %>% 
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  
  mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.))

forest_ind_fig_surv <- forest_ind_surv %>% 
  ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")
forest_ind_fig_surv

# ggsave("Figures/Figure 1C Forest plot MVA indexed full model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 6,
#        height = 5, compression = "lzw"
#        )

forest_surv_fullmva <- 
  forest_prop_surv %>%
  mutate(approach = "Proportion") %>% 
  bind_rows(., forest_ind_surv %>%
  mutate(approach = "Indexed")) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>% 
  mutate(Characteristic = factor(Characteristic, 
                                 levels = c("IMAT",
                                            "VAT",
                                            "SAT",
                                            "SMI", "CH"
                                 ))) %>% 
  ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ approach, axes = "all",
             # scales = "free_x",
             strip.position = "right")
forest_surv_fullmva

# ggsave("Figures/Figure 1 C-D Forest plot MVA full model20260407.tiff",
#        dpi = 600, units = "in",
#        width = 6,
#        height = 5, compression = "lzw"
#        )
```

```{r patchwork HR forest}
library(patchwork)

forest_mva_ind_surv <- forest_mva_ind_surv +
  labs(subtitle = 'Indexed')
forest_mva_prop_surv <- forest_mva_prop_surv +
  labs(subtitle = 'Proportion')

(forest_mva_ind_surv + forest_mva_prop_surv) /
  (forest_surv_fullmva) + plot_annotation(tag_levels = 'A')+
  plot_layout(heights = unit(c(2, 1), c('null', 'null')))

# ggsave("Figures/Figure 1 Forest plot20260407.tiff",
#        dpi = 600, units = "in",
#        width = 8,
#        height = 6, compression = "lzw"
#        )
```
<br>















Other
```{r}
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + tat_cm2_indexsdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + v_s_ratio,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + visceral_obesity,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + sarcopenia,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + ch_status + myosteatosis,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```



```{r}
# tbl_3 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           smi + vat_cm2_index + sat_cm2_index + imat_cm2_index,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# tbl_4 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl_merge(list(tbl_3, tbl_4), tab_spanner = c("**Multivariable \nBody Comp \nIndexed**",
#                                               "**Multivariable \nBody Comp \nProportion**"))
# 
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           v_s_ratio_tertcat,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
```

<!-- Additionally adjusted by BMI -->
<!-- ```{r} -->
<!-- coxph(Surv(time = lymphoma_data$os_time_from_treatment_months, -->
<!--              event = lymphoma_data$os_event) ~ age_at_diagnosis_num + -->
<!--           sex + race + ch_status + -->
<!--           muscle_proportion + vat_proportion + sat_proportion + imat_proportion +  -->
<!--         bmi, -->
<!--         data = lymphoma_data)  %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% -->
<!--   bold_p(t = .05) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- ``` -->

## KM by CH
```{r KM OS by CH}
ggsurvplot(survfit(Surv(os_time_from_treatment_months, os_event) ~ ch_status,
                   data = lymphoma_data),
           # title = "PFS Analysis",
           font.main = c(20, "bold", "black"),
           font.x = c(18, "bold", "black"),
           font.y = c(18, "bold", "black"),
           font.legend = c(16, "black"),
           font.tickslab = c(16, "bold", "black"),
           size = 1.5,

           xlab = "Time (months)",
           legend = "top",
           pval = TRUE,
           conf.int = FALSE,
           # Censor
           censor = TRUE
) %++% guides(colour = guide_legend(ncol = 1))
```


<br>

# L-CH
```{r}
lymphoma_data %>% 
  filter(patient_l_ch == "L-CH") %>% 
  inner_join(., ch_mutation) %>% 
  select(mrn, gene, variant_p, os_event, os_time_from_treatment_months, sex, race, ethnicity_src_desc, myosteatosis, sarcopenia, bmi)
```



***

sessionInfo available in Readme file

```{r}
sessionInfo() %>% capture.output(file="readme_sessioninfo.txt")
```





