---
title: "Lymphoma obesity analysis using VAF ≥ 0.02 to classify CH"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: kable
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library, echo = FALSE}
library(tidyverse)
library(labelled)
library(gtsummary)
library(gt)
library(survminer)
library(survival)
library(patchwork)
theme_gtsummary_compact()
theme_set(theme_classic())
```

<style>
div.darkblue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">CH in Lymphoma and obesity analysis</span>

</div>
<br>

```{r load}
lymphoma_data <- read_rds(paste0(here::here(), 
                            "/data/processed data",
                            "/LymphomaObesity_Data_20260629.rds")) %>% 
  select(-ch_status)
path <- fs::path("", "Volumes", "Gillis_Research",
                 "Lab_Data", "LymphomaObesity")
sample_list <- 
  readxl::read_xlsx(paste0(# path,
    here::here(), "/data/raw data",
    "/Lymphoma_Shipping Manifest_EXP2052DNA_PHI_20240504.xlsx"), 
    sheet = "Shipping Manifest_w PHI") %>% 
  janitor::clean_names()
ch_mutation <- 
  readxl::read_xlsx(paste0(# path,
    here::here(), "/data/raw data",
    "/Lymphoma_CHcalls_20260417.xlsx"), 
    na = "NA") %>% 
  janitor::clean_names()

drug_dat <- 
  readxl::read_xlsx(paste0(# path,
    here::here(), "/data/raw data",
    "/Lymphoma_DrugDataEHR_20260701.xlsx"), na = "NA") %>% 
  janitor::clean_names() %>% 
  filter(is.na(exclude)) %>% 
  select(mrn, regimen, regimen_start = start, regimen_stop = stop, 
         progression_date = progression, last_prog_fu, notes)
```

```{r}
lymphoma_data <- lymphoma_data %>% 
  mutate(race = factor(race, levels = c("White", "Other"))) %>% 
  mutate(ethnicity_src_desc = na_if(ethnicity_src_desc, "UNKNOWN")) |> 
  mutate(ethnicity_src_desc = case_when(
    is.na(ethnicity_src_desc)            ~ "SPANISH NOS",
    TRUE                                 ~ ethnicity_src_desc
  )) %>% 
  mutate(year_at_dx = year(dx_dt)) %>% 
  mutate(year_at_dx_cat = case_when(
    year_at_dx >= 2011 &
      year_at_dx <= 2017                  ~ "2011-2017",
    year_at_dx >= 2018 &
      year_at_dx <= 2022                  ~ "2018-2012",
    TRUE                                  ~ as.character(year_at_dx)
  )) %>% 
  mutate(stage1 = case_when(
    str_detect(stage_tnm_cs_mixed_group_desc, "1")   ~ "I",
    str_detect(stage_tnm_cs_mixed_group_desc, "2")   ~ "II",
    str_detect(stage_tnm_cs_mixed_group_desc, "3")   ~ "III",
    str_detect(stage_tnm_cs_mixed_group_desc, "4")   ~ "IV"
  )) %>% 
  mutate(stage = case_when(
    stage1 %in% c("I", "II")              ~ "I-II",
    stage1 %in% c("III", "IV")            ~ "III-IV"
  )) %>% 
  left_join(., drug_dat %>% 
              mutate(mrn = as.character(mrn)),
            by = "mrn") %>% 
  mutate(progression_date = as.Date(as.numeric(progression_date), origin = "1899-12-30")) %>% 
  mutate(pfs_event = case_when(
    !is.na(progression_date)         ~ 1,
    os_event == 1                    ~ 1,
    os_event == 0                    ~ 0
  )) %>% 
  mutate(pfs_date = case_when(
    !is.na(progression_date)         ~ progression_date,
    os_event == 1                    ~ last_prog_fu,
    os_event == 0                    ~ last_prog_fu
  )) %>% 
  mutate(pfs_time_from_treatment_months = interval(start = regimen_start, end = pfs_date) /
           duration(n=1, unit = "months")) %>% 
  
  # select(mrn, progression_date, pfs_event, pfs_date, pfs_time_from_treatment_months, os_event, os_time_from_treatment_months,
  #        date_of_last_contact, last_prog_fu, notes) %>% 
  # mutate(last_prog_fu == date_of_last_contact)
  
  mutate(regimen_cat = case_when(
    str_detect(regimen, "CHOP")        ~ "R-CHOP",
    str_detect(regimen, "EPOCH")       ~ "DA-EPOCH-R"
  )) %>% 
  mutate(time_sample_first_treatment = interval(start = first_treatment_dt, end = collection_dt_germline) /
           duration(n=1, unit = "days")) #%>% 
  # select(mrn, first_treatment_dt, collection_dt_germline)

lymphoma_data <- lymphoma_data %>% 
  # Index
  mutate(across(c(ends_with("_cm2")
                  ), ~ . / (height_m ^2), 
                .names = "{.col}_index")) %>% 
  rename(smi = muscle_cm2_index) %>% 
  # Sarcopenia
  mutate(sarcopenia = case_when(
    sex == "Female" &
      smi >= 38.5                         ~ "≥ cutoff",
    sex == "Female" &
      smi < 38.5                          ~ "Sarcopenia",
    sex == "Male" &
      smi >= 52.4                         ~ "≥ cutoff",
    sex == "Male" &
      smi < 52.4                          ~ "Sarcopenia"
  )) %>%
  # Myosteatosis - skeletal muscle fat infiltration
  mutate(myosteatosis = case_when(
    bmi < 25 &
      muscle_hu < 41                      ~ "Myosteatosis",
    bmi >= 25 &
      muscle_hu < 33                      ~ "Myosteatosis",
    !is.na(muscle_hu) &
      !is.na(bmi)                         ~ "No myosteatosis"
  ), myosteatosis = factor(myosteatosis, levels = c("No myosteatosis", "Myosteatosis"))) %>%
  # TAT
  mutate(tat_cm2 = case_when(
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                       ~ NA_real_,
    TRUE                                  ~ vat_cm2 + sat_cm2 + imat_cm2
  )) %>% 
  mutate(tat_cm2_index = case_when(
    is.na(vat_cm2_index) |
    is.na(sat_cm2_index) |
    is.na(imat_cm2_index)                 ~ NA_real_,
    TRUE                                  ~ vat_cm2_index + sat_cm2_index + imat_cm2_index
  )) %>% 
  # V/S ratio
  mutate(v_s_ratio = vat_cm2 / sat_cm2) %>% 
  mutate(visceral_obesity = case_when(
    v_s_ratio > 0.4                       ~ "Viscerally obese",
    !is.na(v_s_ratio)                     ~ "Not viscerally obese"
  )) %>% 
  # Proportion - remove the values if one feature is NA
  mutate(muscle_proportion = muscle_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(vat_proportion = vat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(sat_proportion = sat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  mutate(imat_proportion = imat_cm2 / 
           (muscle_cm2 + vat_cm2 +
              sat_cm2 + imat_cm2)) %>% 
  # mutate(muscle_proportionindex = smi / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(vat_proportionindex = vat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(sat_proportionindex = sat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  # mutate(imat_proportionindex = imat_cm2_index / 
  #          (smi + vat_cm2_index +
  #             sat_cm2_index + imat_cm2_index)) %>% 
  mutate(across(c(contains("_proportion")), ~ case_when(
    is.na(muscle_cm2) |
    is.na(vat_cm2) |
    is.na(sat_cm2) |
    is.na(imat_cm2)                    ~ NA_real_,
    TRUE                               ~ .
  )))

lymphoma_data <- lymphoma_data %>% 
  # Make categorical var
  mutate(across(c(smi, ends_with("_index"),
                  "muscle_hu",
                  "vat_cm2", "sat_cm2", "imat_cm2",
                  "tat_cm2",
                  "v_s_ratio",
                  contains("_proportion")
                  ), ~ case_when(
    ntile(., 3) == 1 ~ "Low",
    ntile(., 3) == 2 ~ "Medium",
    ntile(., 3) == 3 ~ "High"),
    .names = "{.col}_tertcat")) %>% 
  mutate(across(c(ends_with("_tertcat")), 
                ~ factor(., levels = 
                           c("Low", "Medium", "High"))))
```


```{r}
# lymphoma_data <- lymphoma_data %>% 
#   # Make 1-standard deviation increase of the height indexed feature
#   mutate(across(c("muscle_hu", "muscle_cm2",
#                   "vat_cm2", "sat_cm2", "imat_cm2",
#                   "tat_cm2"#,
#                   # contains("_proportion")
#                   ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}_sdhr"))

lymphoma_data <- lymphoma_data %>% 
  # Make 1-standard deviation z score
  mutate(across(c("smi", "muscle_hu",
                  "vat_cm2_index", "sat_cm2_index", "imat_cm2_index",
                  "tat_cm2_index"#,
                  # contains("_proportion")
                  ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}_sdhr"))
  # group_by(sex) %>% 
  # mutate(across(c("muscle_hu", "smi",
  #                 "vat_cm2_index", "sat_cm2_index", "imat_cm2_index",
  #                 "tat_cm2_index",
  #                 ends_with("_proportion")
  #                 ), ~ mean(., na.rm = TRUE) , .names = "{.col}_mean")) %>% 
  # mutate(across(c("muscle_hu", "smi",
  #                 "vat_cm2_index", "sat_cm2_index", "imat_cm2_index",
  #                 "tat_cm2_index",
  #                 ends_with("_proportion")
  #                 ), ~ sd(., na.rm = TRUE) , .names = "{.col}_sd")) %>% 
  # ungroup() %>% 
  # mutate(muscle_hu_sdhr = (muscle_hu - muscle_hu_mean) / muscle_hu_sd) %>% 
  # mutate(smi_sdhr = (smi - smi_mean) / smi_sd) %>% 
  # mutate(vat_cm2_index_sdhr = (vat_cm2_index - vat_cm2_index_mean) / vat_cm2_index_sd) %>% 
  # mutate(sat_cm2_index_sdhr = (sat_cm2_index - sat_cm2_index_mean) / sat_cm2_index_sd) %>% 
  # mutate(imat_cm2_index_sdhr = (imat_cm2_index - imat_cm2_index_mean) / imat_cm2_index_sd) %>% 
  # mutate(tat_cm2_index_sdhr = (tat_cm2_index - tat_cm2_index_mean) / tat_cm2_index_sd) %>% 
  # mutate(muscle_proportion_sdhr = (muscle_proportion - muscle_proportion_mean) / muscle_proportion_sd) %>% 
  # mutate(vat_proportion_sdhr = (vat_proportion - vat_proportion_mean) / vat_proportion_sd) %>% 
  # mutate(sat_proportion_sdhr = (sat_proportion - sat_proportion_mean) / sat_proportion_sd) %>% 
  # mutate(imat_proportion_sdhr = (imat_proportion - imat_proportion_mean) / imat_proportion_sd) #%>% 
  
  # select(mrn, sex, contains("imat"), -contains("tertcat"))
  

lymphoma_data <- lymphoma_data %>%
  # Make 1-standard deviation increase of the height indexed feature
  mutate(across(c(contains("_proportion") & where(is.numeric)
                  ), ~ . / sd(., na.rm = TRUE) , .names = "{.col}_sdhr"))
```

```{r}
ch_mutation <- ch_mutation %>% 
  # Filter VAF
  mutate(ch_status = case_when(
    ch_status == "No CH"              ~ "No CH",
    vaf >= 0.02                       ~ "CH"
  )) |> 
  group_by(patient_id) |> 
  fill(ch_status) |> 
  mutate(n = n()) |> 
  ungroup() |> 
  filter(ch_status == "CH" |
           ch_status == "No CH" |
           (is.na(ch_status)) & n == 1) |> 
  mutate(ch_status = case_when(
    ch_status == "No CH"              ~ "No CH",
    ch_status == "CH"                 ~ "CH",
    is.na(ch_status)                  ~ "No CH"
  )) |> 
  select(-n) |> 
  mutate(across(c(where(is.character), where(is.logical),
                  -c("patient_id", "ch_status",
                     "study_id", "source_sample_id"
                  )),
                ~ case_when(
                  ch_status == "No CH"              ~ NA_character_,
                  ch_status == "CH"                 ~ as.character(.)
                ))) |> 
  mutate(across(c(where(is.numeric),
                  -c("patient_id", "ch_status",
                     "study_id", "source_sample_id"
                  )),
                ~ case_when(
                  ch_status == "No CH"              ~ NA_real_,
                  ch_status == "CH"                 ~ as.numeric(.)
                ))) |> 
  inner_join(sample_list %>%
              select(source_sample_id, mrn) %>%
              distinct(), .,
            by = "source_sample_id") %>%
  mutate(mrn = as.character(mrn)) %>%
  mutate(patient_l_ch = case_when(
    l_ch == "TRUE"                     ~ "L-CH"
  )) %>% 
  group_by(mrn) %>%
  mutate(number_of_mutation_per_patient = case_when(
    is.na(gene)                        ~ NA_real_,
    TRUE                               ~ n()
  )) %>% 
  fill(patient_l_ch, .direction = "updown") %>% 
  ungroup()

library(fastDummies)
ch_mutation1 <- ch_mutation %>% 
  filter(!is.na(gene)) %>% 
  select(mrn, number_of_mutation_per_patient, gene, variant_p) %>% 
  unite(mutation_variant, c(gene, variant_p)) %>%
  distinct()

mutation_variant_wide <- dummy_cols(.data = ch_mutation1, select_columns = "mutation_variant",
                                    remove_selected_columns = TRUE,
                                    omit_colname_prefix = FALSE, ignore_na = TRUE) %>%
  group_by(mrn, number_of_mutation_per_patient) %>%
  summarise(across(everything(), sum)) %>%
  ungroup()

ch_mutation1 <- ch_mutation %>% 
  filter(!is.na(gene)) %>% 
  select(mrn, mutation_gene = gene) %>% 
  distinct()

mutation_gene_wide <- dummy_cols(.data = ch_mutation1, select_columns = "mutation_gene",
                                    remove_selected_columns = TRUE,
                                    omit_colname_prefix = FALSE, ignore_na = TRUE) %>%
  group_by(mrn) %>%
  summarise(across(everything(), sum)) %>%
  ungroup()

lymphoma_data <- lymphoma_data %>%
  inner_join(., ch_mutation %>% 
               select(mrn, ch_status, patient_l_ch) %>% 
               distinct(), 
             by = "mrn") %>%
  full_join(., mutation_variant_wide, by = "mrn") %>%
  full_join(., mutation_gene_wide, by = "mrn") %>%
  mutate(across(c(starts_with("mutation_variant") | 
                    starts_with("mutation_gene")
                  ), .fns = ~ replace_na(., 0))) %>% 
  mutate(ch_status = factor(ch_status, levels = c("No CH", "CH")))
```

```{r Labeling data}
var_label(lymphoma_data) <- list(age_at_diagnosis_num = "Patient age",
                                 year_at_dx_cat = "Year of diagnosis",
                                 time_sample_first_treatment = "Time from sample to first treatment (days)",
                                 sex = "Sex",
                                 race_cr_src_desc_1	 = "Race (raw)",
                                 race = "Race", ethnicity_src_desc = "Ethnicity",
                                 histology_desc = "Histology",
                                 stage = "Stage",
                                 bmi = "BMI (kg/m², continuous)",
                                 bmi_cat = "BMI (kg/m², categorical)",
                                 bsa_du_bois = "BSA (Dubois formula)",
                                 bsa_cat = "BSA (categorical)",
                                 weight_kg = "Weight (kg)",
                                 height_m = "Height (m)",
                                 regimen_cat = "First course treatment",
                                 v_s_ratio = "V/S ratio",
                                 visceral_obesity = "Visceral obesity",
                                 tat_cm2 = "TAT",
                                 smi = "SMI",
                                 sarcopenia = "Sarcopenia",
                                 vat_cm2_index = "VATI",
                                 sat_cm2_index = "SATI",
                                 imat_cm2_index = "IMATI",
                                 tat_cm2_index = "TATI",
                                 muscle_proportion = "Muscle proportion",
                                 vat_proportion = "VAT proportion",
                                 sat_proportion = "SAT proportion",
                                 imat_proportion = "IMAT proportion",
                                 
                                 smi_sdhr = "SMI",
                                 vat_cm2_index_sdhr = "VATI",
                                 sat_cm2_index_sdhr = "SATI",
                                 imat_cm2_index_sdhr = "IMATI",
                                 tat_cm2_index_sdhr = "TATI",
                                 muscle_proportion_sdhr = "Muscle proportion",
                                 vat_proportion_sdhr = "VAT proportion",
                                 sat_proportion_sdhr = "SAT proportion",
                                 imat_proportion_sdhr = "IMAT proportion",
                                 
                                 os_event = "Deaths",
                                 # os_time_from_treatment_months = "Follow-up time from treatment (months)",
                                 ch_status = "CH status"
)
```

# I. Patient characteristic by CH status - Table 1
```{r Patient characteristics}
lymphoma_data %>%
  select(ch_status,
         time_sample_first_treatment,
         `survival time (months, Registry)` = survival_time_in_months,
         os_time_from_treatment_months, os_event,
         pfs_event) %>%
  tbl_summary(statistic = list(all_continuous() ~ 
                                 "{median} [{min}-{max}] ({p25}, {p75})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels()
         
lymphoma_data %>%
  select(age_at_diagnosis_num, 
         year_at_dx_cat,
         sex, 
         race, 
         ethnicity_src_desc,
         stage,
         bmi, bmi_cat, #bsa_du_bois, bsa_cat,
         # weight_kg, height_m,
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Patient characteristics**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```

<!-- # II. BMI, Survival and Body composition -->
<!-- It was described that BMI is not the best predictor for survival. While we would expect patients present in the highest BMI group (≥30) to have the worse survival, they often show a better survival than patient within the middle BMI group (≥25 - <30). -->
<!-- ```{r KM OS BMI} -->
<!-- ggsurvplot(survfit(Surv(os_time_from_treatment_months, os_event) ~ bmi_cat, -->
<!--                    data = lymphoma_data), -->
<!--            # title = "PFS Analysis", -->
<!--            font.main = c(20, "bold", "black"), -->
<!--            font.x = c(18, "bold", "black"), -->
<!--            font.y = c(18, "bold", "black"), -->
<!--            font.legend = c(16, "black"), -->
<!--            font.tickslab = c(16, "bold", "black"), -->
<!--            size = 1.5, -->
<!--            palette = c("#000004FF", "#8C2981FF", "#FE9F6DFF"), #"aaas", -->
<!--            xlab = "Time (months)", -->
<!--            legend = "top", -->
<!--            pval = TRUE, -->
<!--            conf.int = FALSE, -->
<!--            # Censor -->
<!--            censor = TRUE -->
<!-- ) %++% guides(colour = guide_legend(ncol = 1)) -->

<!-- coxph(Surv(time = lymphoma_data$os_time_from_treatment_months, -->
<!--              event = lymphoma_data$os_event) ~ bmi_cat, -->
<!--         data = lymphoma_data)  %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% -->
<!--   bold_p(t = .05) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") %>%  -->
<!--   modify_header(label ~ "**Survival association with BMI**") -->
<!-- ``` -->

<!-- Also, BMI is not the best representation of the actual body composition.    -->
<!-- For example, in our cohort, the highest median value for muscle HU (radiodensity) belong to the patients in the middle BMI category (≥25 - <30). -->
<!-- SAT values are similar between these patients and patients in the high BMI category (≥30). -->
<!-- ```{r Body composition plot, fig.height=5} -->
<!-- lymphoma_data %>%  -->
<!--   select(mrn, -->
<!--          muscle_cm2, imat_cm2, vat_cm2, sat_cm2,  -->
<!--          muscle_hu, -->
<!--          bmi_cat -->
<!--          ) %>% -->
<!--   filter(!is.na(bmi_cat)) %>%  -->
<!--   pivot_longer(-c(mrn, bmi_cat)) %>%  -->
<!--   mutate(name = factor(name, levels = c("muscle_hu", "muscle_cm2",  -->
<!--                                         "vat_cm2", "sat_cm2", "imat_cm2"))) %>%  -->
<!--   ggplot(aes(x= bmi_cat, y= value, color = bmi_cat))+ -->
<!--   geom_boxplot()+ -->
<!--   labs(x = "BMI (categories)", y = "Body composition values")+ -->
<!--   scale_color_viridis_d(option = "A", end = c(0.8))+ -->
<!--   theme_classic()+ -->
<!--   coord_flip()+ -->
<!--   # facet_grid(cols = vars(name), scales = "free") -->
<!--   facet_wrap(.~ name, scales = "free", ncol = 2)+ -->
<!--   theme(legend.position = "none") -->
<!-- ``` -->

# III. Body composition features by CH status - Table 1

Most patients (82) have thickness of 3.75 which is often used for Pet/CT so this looks normal. A couple of patient have smaller thickness and 12 have higher thickness value.   

<br>

Dan suggested to :   
- Calculate indexed feature (variables need to be divided by height^2).  
- Look at sarcopenia (sarcopenia was defined as muscle indexed [SMI] < 52.4 cm2/m2 for males and SMI < 38.5 cm2/m2 for females).   
- Look at muscle_hu are Hounsfield unit and measure radiodensity. It is important in case of oedema, scaring. It is muscle radiomics, it reflect the muscle quality.    
- Calculate V/S ratio which is VAT divided by SAT.  
- Visceral obesity category (visceral obese have a V/S ratio > 0.4).  
- Calculate TAT or total fat tissue (VAT+SAT+IMAT).   
- Calculate tissue proportion (for variable A, we divide variable A by the sum of all the tissue combined muscle+VAT+SAT+IMAT).   
Another thing done in papers is that they used 1-standard deviation increase (z-score) of the feature in the Cox regression model.

<br>

```{r}
lymphoma_data %>%
  select(smi, sarcopenia, sex
         ) %>%
  tbl_summary(by = sex,
              statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**SMI by sex**",
                all_stat_cols() ~ "**{level}**, N = {n}")
```


```{r Body composition table}
tbl_raw <- lymphoma_data %>%
  select(#muscle_cm2, imat_cm2, vat_cm2, sat_cm2, 
         muscle_hu, myosteatosis, sarcopenia,
         v_s_ratio, visceral_obesity, #tat_cm2,
         # ends_with("_tertcat"),
         # imat_hu, vat_hu, sat_hu,
         # muscle_sd, imat_sd, vat_sd,
         # sat_sd,
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_sdhr <- lymphoma_data %>%
#   select(ends_with("_sdhr"), 
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")

tbl_index <- lymphoma_data %>%
  select(smi, 
         vat_cm2_index, sat_cm2_index, imat_cm2_index, #tat_cm2_index, 
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_index_sdhr <- lymphoma_data %>%
#   select(ends_with("_index_sdhr"), 
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} [{sd}] ({p25}, {p75})", 
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")

tbl_prop <- lymphoma_data %>%
  select(ends_with("_proportion"),
         ch_status
         ) %>%
  tbl_summary(by = ch_status,
              statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", 
                               all_categorical() ~"{n} ({p}%)")) %>%
  bold_labels() %>%
  add_p() %>% bold_p(t = 0.05) %>% add_overall() %>% 
  modify_header(label ~ "**Body composition**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# tbl_propindex <- lymphoma_data %>% # Using height indexed values generate more missing data if height is NA
#   select(ends_with("_proportionindex"),
#          ch_status
#          ) %>%
#   tbl_summary(by = ch_status,
#               statistic = list(all_continuous() ~ "{median} [{sd}] ({min}, {max})",
#                                all_categorical() ~"{n} ({p}%)")) %>%
#   bold_labels() %>%
#   add_p() %>% bold_p(t = 0.05) %>% add_overall() %>%
#   modify_header(label ~ "**Body composition**",
#                 all_stat_cols() ~ "**{level}**, N = {n}")
```


```{r gt table}
gt_tbl <- tbl_stack(list(tbl_index, tbl_prop, tbl_raw), 
                    group_header = c("Indexed features", 
                                     "Tissue proportion",
                                     "Raw features"
                                     )) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

<!-- I plotted the original features by CH status. Will update once we figure out the best features to show. Figure 3 -->
<!-- ```{r Body composition plot by CH, fig.height=4} -->
<!-- # facet_names <- as_labeller(c( -->
<!-- #   "SMI" = "SMI", -->
<!-- #   "VATI" = "VAT[i]", "SATI" = "SAT[i]", "IMATI" = "IMAT[i]"),  -->
<!-- #   default = label_parsed -->
<!-- # ) -->
<!-- boxplot_index <- lymphoma_data %>%  -->
<!--   select(mrn, -->
<!--          smi, imat_cm2_index, vat_cm2_index, sat_cm2_index,  -->
<!--          # muscle_hu, -->
<!--          bmi_cat, -->
<!--          ch_status -->
<!--          ) %>% -->
<!--   pivot_longer(-c(mrn, bmi_cat, ch_status)) %>%  -->
<!--   mutate(name = case_when( -->
<!--     name == "smi"                         ~ "SMI", -->
<!--     name == "vat_cm2_index"               ~ "VATI", -->
<!--     name == "sat_cm2_index"               ~ "SATI", -->
<!--     name == "imat_cm2_index"              ~ "IMATI" -->
<!--   )) %>% -->
<!--   mutate(name = factor(name, -->
<!--                        levels = c("SMI", "VATI", "SATI", "IMATI")#, -->
<!--                        # labels = c("'Group A'*^1", "'Group B'*^2", "SATI", "IMATI") -->
<!--                        )) %>% -->
<!--   ggplot(aes(x= ch_status, y= value, color = ch_status))+ -->
<!--   geom_boxplot()+ -->
<!--   labs(x = NULL, y = "Body composition values")+ -->
<!--   scale_color_viridis_d(option = "G", end = c(0.8))+ -->
<!--   theme_classic()+ -->
<!--   coord_flip()+ -->
<!--   # facet_grid(cols = vars(name), scales = "free") -->
<!--   facet_wrap(.~ name, scales = "free", nrow = 1)+ -->
<!--   theme(legend.position = "none") -->

<!-- boxplot_prop <- lymphoma_data %>%  -->
<!--   select(mrn, -->
<!--          ends_with("_proportion"), -->
<!--          # muscle_hu, -->
<!--          bmi_cat, -->
<!--          ch_status -->
<!--          ) %>% -->
<!--   pivot_longer(-c(mrn, bmi_cat, ch_status)) %>%  -->
<!--   mutate(name = case_when( -->
<!--     name == "muscle_hu"                    ~ "Muscle density (HU)",  -->
<!--     name == "muscle_proportion"            ~ "Muscle proportion", -->
<!--     name == "vat_proportion"               ~ "VAT proportion",  -->
<!--     name == "sat_proportion"               ~ "SAT proportion",  -->
<!--     name == "imat_proportion"              ~ "IMAT proportion" -->
<!--   )) %>%  -->
<!--   mutate(name = factor(name, levels = c("Muscle density (HU)", "Muscle proportion", -->
<!--                                         "VAT proportion", "SAT proportion",  -->
<!--                                         "IMAT proportion"))) %>% -->
<!--   ggplot(aes(x= ch_status, y= value, color = ch_status))+ -->
<!--   geom_boxplot()+ -->
<!--   labs(x = NULL, y = "Body composition values")+ -->
<!--   scale_color_viridis_d(option = "G", end = c(0.8))+ -->
<!--   theme_classic()+ -->
<!--   coord_flip()+ -->
<!--   # facet_grid(cols = vars(name), scales = "free") -->
<!--   facet_wrap(.~ name, scales = "free", nrow = 1)+ -->
<!--   theme(legend.position = "none") -->

<!-- boxplot_index <- boxplot_index + -->
<!--   labs(subtitle = 'Height-Indexed') -->
<!-- boxplot_prop <- boxplot_prop + -->
<!--   labs(subtitle = 'Proportion') -->

<!-- library(patchwork) -->
<!-- boxplot_index / -->
<!--   boxplot_prop + -->
<!--   plot_layout(axes = "collect") -->



<!-- # ggsave("Figures/Figure S2 Distribution of body composition features by CH status_20260720.jpeg", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 10, -->
<!-- #        height = 4 -->
<!-- #        ) -->
<!-- ``` -->


# IV. CH and Body composition - glm logistic regression

## 1. Regression for association with CH status

### a. BMI - Table S3
https://ashpublications.org/blood/article/144/Supplement%201/872/531065/Mutation-Specific-Differences-in-the-Relationship
In UKBB analyses, we identified genotype-specific patterns of association between BMI and the presence of CH mutations. JAK2 (OR 0.51; 95% CI 0.27-0.96; p=0.036) and DNMT3A mutations (OR 0.92; 95% CI 0.87-0.97; p=0.0028) were negatively associated with a BMI >30 relative to BMI <25, whereas mutations in ASXL1(OR 1.40; 95% CI 1.23-1.60; p=8.8x10-7) and TET2 (OR 1.16; 95% CI 1.04-1.31; p=0.0095) were positively associated with BMI >30.

```{r}
glm(ch_status ~
      age_at_diagnosis_num + sex + stage + bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      age_at_diagnosis_num + sex + stage + bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
```

<!-- BMI overweight and obese combined together -->
<!-- ```{r} -->
<!-- lymphoma_data <- lymphoma_data %>%  -->
<!--   mutate(bmi_cat_grouped = case_when( -->
<!--     bmi_cat == "<25"                ~ "<25", -->
<!--     !is.na(bmi_cat)                 ~ "≥25" -->
<!--   ), bmi_cat_grouped = factor(bmi_cat_grouped, levels = c("<25", "≥25"))) -->

<!-- glm(ch_status ~ -->
<!--       age_at_diagnosis_num + sex + stage + bmi_cat_grouped, -->
<!--     family = "binomial", -->
<!--     data = lymphoma_data) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for CH status") -->
<!-- glm(ch_status ~ -->
<!--       bmi_cat_grouped, -->
<!--     family = "binomial", -->
<!--     data = lymphoma_data) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for CH status") -->
<!-- ``` -->


### b. Association with height-indexed body composition features
#### UVA - Table S4
```{r}
tbl_ch_muscle_ind_uva <- 
  glm(ch_status ~
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_ind_uva
tbl_ch_vat_ind_uva <- 
  glm(ch_status ~
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_ind_uva
tbl_ch_sat_ind_uva <- 
  glm(ch_status ~
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_ind_uva
tbl_ch_imat_ind_uva <- 
  glm(ch_status ~
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_ind_uva
```

#### MVA - Table 2
```{r}
tbl_ch_muscle_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_ind_mva
tbl_ch_vat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_ind_mva
tbl_ch_sat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_ind_mva
tbl_ch_imat_ind_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_ind_mva
```


### c. Association with body composition proportion
#### UVA - Table S4
```{r}
tbl_ch_muscle_prop_uva <- 
  glm(ch_status ~
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_prop_uva
tbl_ch_vat_prop_uva <- 
  glm(ch_status ~
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_prop_uva
tbl_ch_sat_prop_uva <- 
  glm(ch_status ~
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_prop_uva
tbl_ch_imat_prop_uva <- 
  glm(ch_status ~
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_prop_uva
```

#### MVA - Table S5
```{r}
tbl_ch_muscle_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_muscle_prop_mva
tbl_ch_vat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_vat_prop_mva
tbl_ch_sat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_sat_prop_mva
tbl_ch_imat_prop_mva <- 
  glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
tbl_ch_imat_prop_mva
```

### d. Association with others
```{r}
glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          muscle_hu_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          myosteatosis,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
glm(ch_status ~
      age_at_diagnosis_num + sex + stage +
          sarcopenia,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for CH status")
# glm(ch_status ~
#       age_at_diagnosis_num + sex + stage +
#           tat_cm2_index_sdhr,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE
#                  ) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
# glm(ch_status ~
#       age_at_diagnosis_num + sex + stage +
#           v_s_ratio,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE
#                  ) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
# glm(ch_status ~
#       age_at_diagnosis_num + sex + stage +
#           visceral_obesity,
#     family = "binomial",
#     data = lymphoma_data) %>%
#   tbl_regression(exponentiate = TRUE
#                  ) %>%
#   modify_spanning_header(everything() ~ "Regression for CH status")
```
<br>

## 2. Regression for association with CH gene mutations
### a. Count table and VAF - Text values
```{r}
lymphoma_data %>%
  select(number_of_mutation_per_patient, starts_with("mutation_gene")) %>%
  `colnames<-`(str_remove_all(colnames(.), "mutation_gene_")) %>% 
  tbl_summary() %>%
  bold_labels() %>% 
  modify_header(label ~ "**CH mutations**",
                all_stat_cols() ~ "**{level}**, N = {n}")

# lymphoma_data %>%
#   filter(!is.na(number_of_mutation_per_patient)) |> 
#   select(number_of_mutation_per_patient, bmi, bmi_cat) |> 
#   ggplot(aes(x = as.factor(number_of_mutation_per_patient), y = bmi, 
#              color = as.factor(number_of_mutation_per_patient)))+
#   geom_boxplot(outlier.shape = NA)+
#   geom_jitter(color = "grey")+
#   labs(x = "Number of CH mutations per patient")+
#   scale_color_viridis_d(option = "A", end = c(0.6))+
#   theme(legend.position = "none")
         
ch_mutation %>% 
  select(vaf, depth) %>% 
  tbl_summary() %>% 
  bold_labels()
```

### b. BMI
#### UVA - Table S3
```{r}
glm(mutation_gene_DNMT3A ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_DNMT3A ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_PPM1D ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_PPM1D ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_TET2 ~
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
glm(mutation_gene_TET2 ~
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
```

#### MVA - Table S3
```{r}
glm(mutation_gene_DNMT3A ~ age_at_diagnosis_num + sex + stage +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_DNMT3A ~ age_at_diagnosis_num + sex + stage +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
glm(mutation_gene_PPM1D ~ age_at_diagnosis_num + sex + stage +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_PPM1D ~ age_at_diagnosis_num + sex + stage +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
glm(mutation_gene_TET2 ~ age_at_diagnosis_num + sex + stage +
      bmi,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
glm(mutation_gene_TET2 ~ age_at_diagnosis_num + sex + stage +
      bmi_cat,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
```

### c. Association with height-indexed body composition features
#### UVA - Table S4
```{r}
tbl_dnmt3a_muscle_ind_uva <- glm(mutation_gene_DNMT3A ~
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat_ind_uva <- glm(mutation_gene_DNMT3A ~
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_sat_ind_uva <- glm(mutation_gene_DNMT3A ~
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_imat_ind_uva <- glm(mutation_gene_DNMT3A ~
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_ppm1d_muscle_ind_uva <- glm(mutation_gene_PPM1D ~
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat_ind_uva <- glm(mutation_gene_PPM1D ~
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_sat_ind_uva <- glm(mutation_gene_PPM1D ~
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_imat_ind_uva <- glm(mutation_gene_PPM1D ~
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_tet2_muscle_ind_uva <- glm(mutation_gene_TET2 ~
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat_ind_uva <- glm(mutation_gene_TET2 ~
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_sat_ind_uva <- glm(mutation_gene_TET2 ~
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_imat_ind_uva <- glm(mutation_gene_TET2 ~
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_muscle_ind_uva <- tbl_merge(list(tbl_dnmt3a_muscle_ind_uva, tbl_ppm1d_muscle_ind_uva, tbl_tet2_muscle_ind_uva),
                        tab_spanner = c("Regression for DNMT3A mutation",
                                        "Regression for PPM1D mutation",
                                        "Regression for TET2 mutation"))
tbl_vat_ind_uva <- tbl_merge(list(tbl_dnmt3a_vat_ind_uva, tbl_ppm1d_vat_ind_uva, tbl_tet2_vat_ind_uva))
tbl_sat_ind_uva <- tbl_merge(list(tbl_dnmt3a_sat_ind_uva, tbl_ppm1d_sat_ind_uva, tbl_tet2_sat_ind_uva))
tbl_imat_ind_uva <- tbl_merge(list(tbl_dnmt3a_imat_ind_uva, tbl_ppm1d_imat_ind_uva, tbl_tet2_imat_ind_uva))

gt_tbl <- tbl_stack(list(tbl_muscle_ind_uva, tbl_vat_ind_uva, tbl_sat_ind_uva, tbl_imat_ind_uva),
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

#### MVA - Table 2
```{r}
tbl_dnmt3a_muscle_ind_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat_ind_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_sat_ind_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_imat_ind_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_ppm1d_muscle_ind_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat_ind_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_sat_ind_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_imat_ind_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_tet2_muscle_ind_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          smi_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat_ind_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          vat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_sat_ind_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          sat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_imat_ind_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          imat_cm2_index_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_muscle_ind_mva <- tbl_merge(list(tbl_dnmt3a_muscle_ind_mva, tbl_ppm1d_muscle_ind_mva, tbl_tet2_muscle_ind_mva), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat_ind_mva <- tbl_merge(list(tbl_dnmt3a_vat_ind_mva, tbl_ppm1d_vat_ind_mva, tbl_tet2_vat_ind_mva))
tbl_sat_ind_mva <- tbl_merge(list(tbl_dnmt3a_sat_ind_mva, tbl_ppm1d_sat_ind_mva, tbl_tet2_sat_ind_mva))
tbl_imat_ind_mva <- tbl_merge(list(tbl_dnmt3a_imat_ind_mva, tbl_ppm1d_imat_ind_mva, tbl_tet2_imat_ind_mva))

gt_tbl <- tbl_stack(list(tbl_muscle_ind_mva, tbl_vat_ind_mva, tbl_sat_ind_mva, tbl_imat_ind_mva), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

```{r forest plot mva ind}
forest_mva_ind <- 
  tbl_dnmt3a_muscle_ind_mva %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("SMI")) %>%
  mutate(model = "SM") %>% mutate(Pred = "DNMT3A") %>% 
  
  bind_rows(., tbl_dnmt3a_vat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VATI")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_sat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SATI")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_imat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMATI")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_ppm1d_muscle_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SMI")) %>%
              mutate(model = "SM") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_vat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VATI")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_sat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SATI")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_imat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMATI")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_tet2_muscle_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SMI")) %>%
              mutate(model = "SM") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_vat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VATI")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_sat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SATI")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_imat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMATI")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_ch_muscle_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SMI")) %>%
              mutate(model = "SM") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_vat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VATI")) %>%
              mutate(model = "VAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_sat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SATI")) %>%
              mutate(model = "SAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_imat_ind_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMATI")) %>%
              mutate(model = "IMAT") %>%  mutate(Pred = "CH")) %>% 
  
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = factor(Characteristic, levels = c("IMATI", 
                                                            "SATI", "VATI", "SMI")))
facet_names <- as_labeller(c(
  "CH" = "CH",
  "DNMT3A" = "italic('DNMT3A')", "PPM1D" = "italic('PPM1D')", "TET2" = "italic('TET2')"), 
  default = label_parsed
)
forest_mva_ind_fig <-
  forest_mva_ind %>% 
  # mutate(Characteristic = case_when(
  #   Characteristic == "VAT"        ~ "VATI",
  #   TRUE   ~ Characteristic
  # )) %>% 
  ggplot(aes(y=Characteristic, x=OR, xmin=lower, xmax=upper)) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="")+
  # theme(text = element_text(size = 15),
  #       axis.title.y = element_blank())
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ Pred, nrow = 1,
             # scales = "free_x", 
             axes = "margins",
             strip.position = "top", labeller = facet_names)
# forest_mva_ind_fig
# ggsave("Figures/Figure 2A Forest plot MVA ind OR model_20260721.tiff",
#        dpi = 600, units = "in",
#        width = 10,
#        height = 3, compression = "lzw"
#        )
```

### d. Association with body composition proportion
#### UVA - Table S4
```{r}
tbl_dnmt3a_muscle_prop_uva <- glm(mutation_gene_DNMT3A ~
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat_prop_uva <- glm(mutation_gene_DNMT3A ~
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_sat_prop_uva <- glm(mutation_gene_DNMT3A ~
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_imat_prop_uva <- glm(mutation_gene_DNMT3A ~
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_ppm1d_muscle_prop_uva <- glm(mutation_gene_PPM1D ~
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat_prop_uva <- glm(mutation_gene_PPM1D ~
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_sat_prop_uva <- glm(mutation_gene_PPM1D ~
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_imat_prop_uva <- glm(mutation_gene_PPM1D ~
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_tet2_muscle_prop_uva <- glm(mutation_gene_TET2 ~
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat_prop_uva <- glm(mutation_gene_TET2 ~
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_sat_prop_uva <- glm(mutation_gene_TET2 ~
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_imat_prop_uva <- glm(mutation_gene_TET2 ~
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_muscle_prop_uva <- tbl_merge(list(tbl_dnmt3a_muscle_prop_uva, tbl_ppm1d_muscle_prop_uva, tbl_tet2_muscle_prop_uva),
                        tab_spanner = c("Regression for DNMT3A mutation",
                                        "Regression for PPM1D mutation",
                                        "Regression for TET2 mutation"))
tbl_vat_prop_uva <- tbl_merge(list(tbl_dnmt3a_vat_prop_uva, tbl_ppm1d_vat_prop_uva, tbl_tet2_vat_prop_uva))
tbl_sat_prop_uva <- tbl_merge(list(tbl_dnmt3a_sat_prop_uva, tbl_ppm1d_sat_prop_uva, tbl_tet2_sat_prop_uva))
tbl_imat_prop_uva <- tbl_merge(list(tbl_dnmt3a_imat_prop_uva, tbl_ppm1d_imat_prop_uva, tbl_tet2_imat_prop_uva))

gt_tbl <- tbl_stack(list(tbl_muscle_prop_uva, tbl_vat_prop_uva, tbl_sat_prop_uva, tbl_imat_prop_uva),
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```


#### MVA - Table S5
```{r}
tbl_dnmt3a_muscle_prop_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for DNMT3A mutation")
tbl_dnmt3a_vat_prop_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_sat_prop_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_dnmt3a_imat_prop_mva <- glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_ppm1d_muscle_prop_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for PPM1D mutation")
tbl_ppm1d_vat_prop_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  add_global_p(keep = TRUE, test = "LR", type = "III", include = vat_proportion_sdhr) |> 
  bold_p()
tbl_ppm1d_sat_prop_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_ppm1d_imat_prop_mva <- glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_tet2_muscle_prop_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          muscle_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p() %>% 
  modify_spanning_header(everything() ~ "Regression for TET2 mutation")
tbl_tet2_vat_prop_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          vat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_sat_prop_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          sat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
tbl_tet2_imat_prop_mva <- glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          imat_proportion_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()

tbl_muscle_prop_mva <- tbl_merge(list(tbl_dnmt3a_muscle_prop_mva, tbl_ppm1d_muscle_prop_mva, tbl_tet2_muscle_prop_mva), 
                        tab_spanner = c("Regression for DNMT3A mutation", 
                                        "Regression for PPM1D mutation", 
                                        "Regression for TET2 mutation"))
tbl_vat_prop_mva <- tbl_merge(list(tbl_dnmt3a_vat_prop_mva, tbl_ppm1d_vat_prop_mva, tbl_tet2_vat_prop_mva))
tbl_sat_prop_mva <- tbl_merge(list(tbl_dnmt3a_sat_prop_mva, tbl_ppm1d_sat_prop_mva, tbl_tet2_sat_prop_mva))
tbl_imat_prop_mva <- tbl_merge(list(tbl_dnmt3a_imat_prop_mva, tbl_ppm1d_imat_prop_mva, tbl_tet2_imat_prop_mva))

gt_tbl <- tbl_stack(list(tbl_muscle_prop_mva, tbl_vat_prop_mva, tbl_sat_prop_mva, tbl_imat_prop_mva), 
                    group_header = c("Muscle", "VAT",
                                     "SAT", "IMAT")) %>% 
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```

```{r}
forest_mva_prop <- 
  tbl_dnmt3a_muscle_prop_mva %>%
  as_tibble() %>% 
  `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
  filter(Characteristic %in% c("Muscle proportion")) %>%
  mutate(model = "SM") %>% mutate(Pred = "DNMT3A") %>% 
  
  bind_rows(., tbl_dnmt3a_vat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VAT proportion")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_sat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SAT proportion")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_dnmt3a_imat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMAT proportion")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "DNMT3A")) %>% 
  
  bind_rows(., tbl_ppm1d_muscle_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("Muscle proportion")) %>%
              mutate(model = "SM") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_vat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VAT proportion")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_sat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SAT proportion")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_ppm1d_imat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMAT proportion")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "PPM1D")) %>% 
  
  bind_rows(., tbl_tet2_muscle_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("Muscle proportion")) %>%
              mutate(model = "SM") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_vat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VAT proportion")) %>%
              mutate(model = "VAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_sat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SAT proportion")) %>%
              mutate(model = "SAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_tet2_imat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMAT proportion")) %>%
              mutate(model = "IMAT") %>% mutate(Pred = "TET2")) %>% 
  
  bind_rows(., tbl_ch_muscle_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("Muscle proportion")) %>%
              mutate(model = "SM") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_vat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("VAT proportion")) %>%
              mutate(model = "VAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_sat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("SAT proportion")) %>%
              mutate(model = "SAT") %>%  mutate(Pred = "CH")) %>% 
  
  bind_rows(., tbl_ch_imat_prop_mva %>%
              as_tibble() %>% 
              `colnames<-`(str_remove_all(colnames(.), "\\*")) %>% 
              filter(Characteristic %in% c("IMAT proportion")) %>%
              mutate(model = "IMAT") %>%  mutate(Pred = "CH")) %>% 
  
  separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>% 
  mutate_at(c("OR", "lower", "upper"), ~ as.numeric(.)) %>% 
  mutate(Characteristic = str_remove_all(Characteristic, " proportion")) %>% 
  mutate(Characteristic = case_when(
    Characteristic == "Muscle"          ~ "SM",
    TRUE                                ~ Characteristic
  )) %>% 
  mutate(Characteristic = factor(Characteristic, levels = c("IMAT", 
                                                            "SAT", "VAT", "SM")))

facet_names <- as_labeller(c(
  "CH" = "CH",
  "DNMT3A" = "italic('DNMT3A')", "PPM1D" = "italic('PPM1D')", "TET2" = "italic('TET2')"), 
  default = label_parsed
)
forest_mva_prop_fig <-
  forest_mva_prop %>% 
  ggplot(aes(y=Characteristic, x=OR, xmin=lower, xmax=upper)) +
  geom_point() + 
  geom_errorbarh(height=.1) +
  geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) +
  theme_classic()+
  scale_x_log10()+
  labs(y="") %>% 
  # theme(text = element_text(size = 15),
  #       axis.title.y = element_blank())
  theme(text = element_text(size = 15),
        axis.title.y = element_blank(), legend.position = "none")+
  facet_wrap(. ~ Pred, nrow = 1,
             # scales = "free_x", 
             axes = "margins",
             strip.position = "top", labeller = facet_names)
# forest_mva_prop_fig
# ggsave("Figures/Figure 2B Forest plot MVA prop OR model_20260721.tiff",
#        dpi = 600, units = "in",
#        width = 10,
#        height = 3, compression = "lzw"
#        )
```


```{r}
library(patchwork)

# forest_mva_ind <- forest_mva_ind# +
#   # labs(subtitle = 'Indexed')
# forest_mva_prop <- forest_mva_prop# +
#   # labs(subtitle = 'Proportion')

# forest_mva_ind_fig /
#   forest_mva_prop_fig + plot_annotation(tag_levels = 'A')+
#   plot_layout(axis_titles = "collect")

# ggsave("Figures/Figure 2 Forest plot MVA OR model_20260721.tiff",
#        dpi = 600, units = "in",
#        width = 9,
#        height = 5, compression = "lzw"
#        )
```

### e. Association with others
```{r}
glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          muscle_hu_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for DNMT3A") %>% 
  bold_p()
glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          myosteatosis,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
glm(mutation_gene_DNMT3A ~
      age_at_diagnosis_num + sex + stage +
          sarcopenia,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
```
<br>

```{r}
glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          muscle_hu_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for PPM1D") %>% 
  bold_p()
glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          myosteatosis,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
glm(mutation_gene_PPM1D ~
      age_at_diagnosis_num + sex + stage +
          sarcopenia,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
```
<br>

```{r}
glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          muscle_hu_sdhr,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for TET2") %>% 
  bold_p()
glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          myosteatosis,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
glm(mutation_gene_TET2 ~
      age_at_diagnosis_num + sex + stage +
          sarcopenia,
    family = "binomial",
    data = lymphoma_data) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  bold_p()
```
<br>




<!-- ## 3. Regression for association with CH variants mutations -->
<!-- ### Count table - Ns are too snmall to do further regression -->
<!-- ```{r} -->
<!-- lymphoma_data %>% -->
<!--   select(starts_with("mutation_variant")) %>% -->
<!--   `colnames<-`(str_remove_all(colnames(.), "mutation_variant_")) %>%  -->
<!--   tbl_summary() %>% -->
<!--   bold_labels() %>%  -->
<!--   modify_header(label ~ "**CH mutations**", -->
<!--                 all_stat_cols() ~ "**{level}**, N = {n}") -->
<!-- ``` -->
<!-- <br> -->

## 4. Regression for association with CH VAF
Select the highest VAF for continuous analysis (log2) or categorize raw VAF as ≥ 0.10 (coded 1) or < 0.10 (coded 0) for binary analysis.
```{r}
vaf_reg_dat <- ch_mutation %>% 
  filter(!is.na(vaf)) %>%
  select(mrn, vaf) %>% 
  arrange(mrn, desc(vaf)) %>% 
  # distinct(mrn, .keep_all = TRUE) |> 
  mutate(log2_vaf = log2(vaf)) %>% 
  mutate(vaf_cat = case_when(
    vaf >= 0.10           ~ 1,
    vaf < 0.10            ~ 0
  )) %>% 
  full_join(lymphoma_data, 
            ., 
            by = "mrn") %>% 
  filter(!is.na(vaf))
```

```{r}
vaf_sa_fig <- 
  vaf_reg_dat |> 
  select(vaf, log2_vaf, bmi, bmi_cat) |> 
  ggplot(aes(x = bmi, y = log2_vaf))+
  geom_point()+
  xlim(15, 50)+
  labs(x = "BMI (kg/m²)", y = "VAF (log2)")+
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  stat_cor(aes(label = paste(..rr.label.., ..p.label.., sep = "~`,`~")), 
           # label.x = 4.5#, 
           label.y = -2.5
           )
# vaf_sa_fig
# ggsave("Figures/Figure Sa VAF_20260803.tiff",
#        dpi = 600, units = "in",
#        width = 5,
#        height = 5, compression = "lzw"
#        )

vaf_sb_fig <-
  vaf_reg_dat |> 
  select(vaf, log2_vaf, bmi, bmi_cat) |> 
  mutate(bmi_cat = case_when(
    bmi_cat == "<25"                    ~ "Under-normal weight",
    bmi_cat == "≥25 - <30"              ~ "Overweight",
    bmi_cat == "≥30"                    ~ "Obese"
  ), bmi_cat = factor(bmi_cat, levels = c("Under-normal weight", "Overweight", "Obese"))) |> 
  ggplot(aes(x = bmi_cat, y = log2_vaf, color = bmi_cat))+
  geom_boxplot()+
  geom_jitter(color = "grey")+
  labs(y = "VAF (log2)")+
  scale_color_viridis_d(option = "G", end = c(0.6),
                        limits = c("Under-normal weight",
                                   "Overweight",
                                   "Obese"), name = "BMI (kg/m²)")+
  # coord_flip()+
  theme(#axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        #axis.ticks.y = element_blank(),
        legend.position = "none")+
  stat_compare_means(comparisons = list(
    c("Under-normal weight", "Overweight"),
    c("Under-normal weight", "Obese"),
    c("Overweight", "Obese")
  ),
  method = "wilcox.test", label = "p.format" )
# vaf_sb_fig
# ggsave("Figures/Figure Sb VAF_20260810.tiff",
#        dpi = 600, units = "in",
#        width = 5,
#        height = 5, compression = "lzw"
#        )


vaf_sa_fig /
  vaf_sb_fig + plot_annotation(tag_levels = 'A')
# ggsave("Figures/Figure_combined Sab VAF_20260810.tiff",
#        dpi = 600, units = "in",
#        width = 5,
#        height = 8, compression = "lzw"
#        )
```


### A. Continuous LOG2 VAF
```{r}
vaf_reg_dat <- ch_mutation %>% 
  filter(!is.na(vaf)) %>%
  select(mrn, vaf) %>% 
  arrange(mrn, desc(vaf)) %>% 
  distinct(mrn, .keep_all = TRUE) |>
  mutate(log2_vaf = log2(vaf)) %>% 
  mutate(vaf_cat = case_when(
    vaf >= 0.10           ~ 1,
    vaf < 0.10            ~ 0
  )) %>% 
  full_join(lymphoma_data, 
            ., 
            by = "mrn") %>% 
  filter(!is.na(vaf))
```

#### a. BMI -Table S5
```{r}
glm(log2_vaf ~
      age_at_diagnosis_num + sex + stage + bmi,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
glm(log2_vaf ~
      bmi,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
glm(log2_vaf ~
      age_at_diagnosis_num + sex + stage + bmi_cat,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
glm(log2_vaf ~
      bmi_cat,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
```


#### b. Association with height-indexed body composition features
#### UVA -Table S5
```{r}
tbl_vaf_muscle_ind_uva <- 
  glm(log2_vaf ~
        smi_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_muscle_ind_uva
tbl_vaf_vat_ind_uva <- 
  glm(log2_vaf ~
        vat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_vat_ind_uva
tbl_vaf_sat_ind_uva <- 
  glm(log2_vaf ~
        sat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_sat_ind_uva
tbl_vaf_imat_ind_uva <- 
  glm(log2_vaf ~
        imat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_imat_ind_uva
```

#### MVA -Table S5
```{r}
tbl_vaf_muscle_ind_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        smi_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_muscle_ind_mva
tbl_vaf_vat_ind_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        vat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_vat_ind_mva
tbl_vaf_sat_ind_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        sat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_sat_ind_mva
tbl_vaf_imat_ind_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        imat_cm2_index_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_imat_ind_mva
```


#### c. Association with body composition proportion
#### UVA
```{r}
tbl_vaf_muscle_prop_uva <- 
  glm(log2_vaf ~
        muscle_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_muscle_prop_uva
tbl_vaf_vat_prop_uva <- 
  glm(log2_vaf ~
        vat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_vat_prop_uva
tbl_vaf_sat_prop_uva <- 
  glm(log2_vaf ~
        sat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_sat_prop_uva
tbl_vaf_imat_prop_uva <- 
  glm(log2_vaf ~
        imat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_imat_prop_uva
```

#### MVA
```{r}
tbl_vaf_muscle_prop_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        muscle_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_muscle_prop_mva
tbl_vaf_vat_prop_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        vat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_vat_prop_mva
tbl_vaf_sat_prop_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        sat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_sat_prop_mva
tbl_vaf_imat_prop_mva <- 
  glm(log2_vaf ~
        age_at_diagnosis_num + sex + stage +
        imat_proportion_sdhr,
      # family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
tbl_vaf_imat_prop_mva
```

#### d. Association with others
```{r}
glm(log2_vaf ~
      age_at_diagnosis_num + sex + stage +
      muscle_hu_sdhr,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
glm(log2_vaf ~
      age_at_diagnosis_num + sex + stage +
      myosteatosis,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")
glm(log2_vaf ~
      age_at_diagnosis_num + sex + stage +
      sarcopenia,
    # family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)")

```


<!-- ### B. Continuous RAW VAF -->
<!-- #### a. BMI -->
<!-- ```{r} -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + stage + bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + stage + bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- ``` -->


<!-- #### b. Association with height-indexed body composition features -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_ind_uva -->
<!-- tbl_vaf_vat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_ind_uva -->
<!-- tbl_vaf_sat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_ind_uva -->
<!-- tbl_vaf_imat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_ind_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_ind_mva -->
<!-- tbl_vaf_vat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_ind_mva -->
<!-- tbl_vaf_sat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_ind_mva -->
<!-- tbl_vaf_imat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_ind_mva -->
<!-- ``` -->


<!-- #### c. Association with body composition proportion -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_prop_uva -->
<!-- tbl_vaf_vat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_prop_uva -->
<!-- tbl_vaf_sat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_prop_uva -->
<!-- tbl_vaf_imat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_prop_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_prop_mva -->
<!-- tbl_vaf_vat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_prop_mva -->
<!-- tbl_vaf_sat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_prop_mva -->
<!-- tbl_vaf_imat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + stage + -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_prop_mva -->
<!-- ``` -->

<!-- #### d. Association with others -->
<!-- ```{r} -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + stage + -->
<!--       muscle_hu_sdhr, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + stage + -->
<!--       myosteatosis, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + stage + -->
<!--       sarcopenia, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->

<!-- ``` -->






### C. Categorical VAF

#### a. BMI - Tanle S5
```{r}
glm(vaf_cat ~
      age_at_diagnosis_num + sex + stage + bmi,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
glm(vaf_cat ~
      bmi,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
glm(vaf_cat ~
      age_at_diagnosis_num + sex + stage + bmi_cat,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
glm(vaf_cat ~
      bmi_cat,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
```


#### b. Association with height-indexed body composition features - Table S5
#### UVA
```{r}
tbl_vaf_muscle_ind_uva <- 
  glm(vaf_cat ~
        smi_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_muscle_ind_uva
tbl_vaf_vat_ind_uva <- 
  glm(vaf_cat ~
        vat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  add_global_p(keep = TRUE, test = "LR", type = "III", include = vat_cm2_index_sdhr) |> 
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_vat_ind_uva
tbl_vaf_sat_ind_uva <- 
  glm(vaf_cat ~
        sat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_sat_ind_uva
tbl_vaf_imat_ind_uva <- 
  glm(vaf_cat ~
        imat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_imat_ind_uva
```

#### MVA
```{r}
tbl_vaf_muscle_ind_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        smi_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_muscle_ind_mva
tbl_vaf_vat_ind_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        vat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  add_global_p(keep = TRUE, test = "LR", type = "III", include = vat_cm2_index_sdhr) |> 
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_vat_ind_mva
tbl_vaf_sat_ind_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        sat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_sat_ind_mva
tbl_vaf_imat_ind_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        imat_cm2_index_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  add_global_p(keep = TRUE, test = "LR", type = "III", include = imat_cm2_index_sdhr) |> 
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_imat_ind_mva
```


#### c. Association with body composition proportion
#### UVA
```{r}
tbl_vaf_muscle_prop_uva <- 
  glm(vaf_cat ~
        muscle_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_muscle_prop_uva
tbl_vaf_vat_prop_uva <- 
  glm(vaf_cat ~
        vat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_vat_prop_uva
tbl_vaf_sat_prop_uva <- 
  glm(vaf_cat ~
        sat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_sat_prop_uva
tbl_vaf_imat_prop_uva <- 
  glm(vaf_cat ~
        imat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_imat_prop_uva
```

#### MVA
```{r}
tbl_vaf_muscle_prop_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        muscle_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_muscle_prop_mva
tbl_vaf_vat_prop_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        vat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_vat_prop_mva
tbl_vaf_sat_prop_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        sat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_sat_prop_mva
tbl_vaf_imat_prop_mva <- 
  glm(vaf_cat ~
        age_at_diagnosis_num + sex + stage +
        imat_proportion_sdhr,
      family = "binomial",
      data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
tbl_vaf_imat_prop_mva
```

#### d. Association with others
```{r}
glm(vaf_cat ~
      age_at_diagnosis_num + sex + stage +
      muscle_hu_sdhr,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
glm(vaf_cat ~
      age_at_diagnosis_num + sex + stage +
      myosteatosis,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")
glm(vaf_cat ~
      age_at_diagnosis_num + sex + stage +
      sarcopenia,
    family = "binomial",
    data = vaf_reg_dat) %>%
  tbl_regression(exponentiate = TRUE
                 ) %>%
  modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10")

```
<br>

<!-- ### A1. Continuous LOG2 VAF - stage -->
<!-- #### a. BMI -->
<!-- ```{r} -->
<!-- glm(log2_vaf ~ -->
<!--       age_at_diagnosis_num + sex + bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- glm(log2_vaf ~ -->
<!--       bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- glm(log2_vaf ~ -->
<!--       age_at_diagnosis_num + sex + bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- glm(log2_vaf ~ -->
<!--       bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- ``` -->


<!-- #### b. Association with height-indexed body composition features -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_muscle_ind_uva -->
<!-- tbl_vaf_vat_ind_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_vat_ind_uva -->
<!-- tbl_vaf_sat_ind_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_sat_ind_uva -->
<!-- tbl_vaf_imat_ind_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_imat_ind_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_muscle_ind_mva -->
<!-- tbl_vaf_vat_ind_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_vat_ind_mva -->
<!-- tbl_vaf_sat_ind_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_sat_ind_mva -->
<!-- tbl_vaf_imat_ind_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_imat_ind_mva -->
<!-- ``` -->


<!-- #### c. Association with body composition proportion -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_muscle_prop_uva -->
<!-- tbl_vaf_vat_prop_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_vat_prop_uva -->
<!-- tbl_vaf_sat_prop_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_sat_prop_uva -->
<!-- tbl_vaf_imat_prop_uva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_imat_prop_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_muscle_prop_mva -->
<!-- tbl_vaf_vat_prop_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_vat_prop_mva -->
<!-- tbl_vaf_sat_prop_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_sat_prop_mva -->
<!-- tbl_vaf_imat_prop_mva <-  -->
<!--   glm(log2_vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- tbl_vaf_imat_prop_mva -->
<!-- ``` -->

<!-- #### d. Association with others -->
<!-- ```{r} -->
<!-- glm(log2_vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       muscle_hu_sdhr, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- glm(log2_vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       myosteatosis, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->
<!-- glm(log2_vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       sarcopenia, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH log2(VAF)") -->

<!-- ``` -->

<!-- ### B1. Continuous RAW VAF - stage -->
<!-- #### a. BMI -->
<!-- ```{r} -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       bmi, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       bmi_cat, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- ``` -->


<!-- #### b. Association with height-indexed body composition features -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_ind_uva -->
<!-- tbl_vaf_vat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_ind_uva -->
<!-- tbl_vaf_sat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_ind_uva -->
<!-- tbl_vaf_imat_ind_uva <-  -->
<!--   glm(vaf ~ -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_ind_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         smi_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_ind_mva -->
<!-- tbl_vaf_vat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_ind_mva -->
<!-- tbl_vaf_sat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_ind_mva -->
<!-- tbl_vaf_imat_ind_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_cm2_index_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_ind_mva -->
<!-- ``` -->


<!-- #### c. Association with body composition proportion -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_prop_uva -->
<!-- tbl_vaf_vat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_prop_uva -->
<!-- tbl_vaf_sat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_prop_uva -->
<!-- tbl_vaf_imat_prop_uva <-  -->
<!--   glm(vaf ~ -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_prop_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         muscle_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_muscle_prop_mva -->
<!-- tbl_vaf_vat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_vat_prop_mva -->
<!-- tbl_vaf_sat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_sat_prop_mva -->
<!-- tbl_vaf_imat_prop_mva <-  -->
<!--   glm(vaf ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_proportion_sdhr, -->
<!--       # family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- tbl_vaf_imat_prop_mva -->
<!-- ``` -->

<!-- #### d. Association with others -->
<!-- ```{r} -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       muscle_hu_sdhr, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       myosteatosis, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->
<!-- glm(vaf ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       sarcopenia, -->
<!--     # family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for continuous CH raw VAF") -->

<!-- ``` -->

<!-- ### C1. Categorical VAF - stage -->

<!-- #### a. BMI -->
<!-- ```{r} -->
<!-- glm(vaf_cat ~ -->
<!--       age_at_diagnosis_num + sex + bmi, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- glm(vaf_cat ~ -->
<!--       bmi, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- glm(vaf_cat ~ -->
<!--       age_at_diagnosis_num + sex + bmi_cat, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- glm(vaf_cat ~ -->
<!--       bmi_cat, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- ``` -->


<!-- #### b. Association with height-indexed body composition features -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         smi_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_muscle_ind_uva -->
<!-- tbl_vaf_vat_ind_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         vat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_vat_ind_uva -->
<!-- tbl_vaf_sat_ind_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         sat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_sat_ind_uva -->
<!-- tbl_vaf_imat_ind_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         imat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_imat_ind_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_ind_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         smi_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_muscle_ind_mva -->
<!-- tbl_vaf_vat_ind_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_vat_ind_mva -->
<!-- tbl_vaf_sat_ind_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_sat_ind_mva -->
<!-- tbl_vaf_imat_ind_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_cm2_index_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_imat_ind_mva -->
<!-- ``` -->


<!-- #### c. Association with body composition proportion -->
<!-- #### UVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         muscle_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_muscle_prop_uva -->
<!-- tbl_vaf_vat_prop_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         vat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_vat_prop_uva -->
<!-- tbl_vaf_sat_prop_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         sat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_sat_prop_uva -->
<!-- tbl_vaf_imat_prop_uva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         imat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_imat_prop_uva -->
<!-- ``` -->

<!-- #### MVA -->
<!-- ```{r} -->
<!-- tbl_vaf_muscle_prop_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         muscle_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_muscle_prop_mva -->
<!-- tbl_vaf_vat_prop_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         vat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_vat_prop_mva -->
<!-- tbl_vaf_sat_prop_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         sat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_sat_prop_mva -->
<!-- tbl_vaf_imat_prop_mva <-  -->
<!--   glm(vaf_cat ~ -->
<!--         age_at_diagnosis_num + sex + -->
<!--         imat_proportion_sdhr, -->
<!--       family = "binomial", -->
<!--       data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- tbl_vaf_imat_prop_mva -->
<!-- ``` -->

<!-- #### d. Association with others -->
<!-- ```{r} -->
<!-- glm(vaf_cat ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       muscle_hu_sdhr, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- glm(vaf_cat ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       myosteatosis, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->
<!-- glm(vaf_cat ~ -->
<!--       age_at_diagnosis_num + sex + -->
<!--       sarcopenia, -->
<!--     family = "binomial", -->
<!--     data = vaf_reg_dat) %>% -->
<!--   tbl_regression(exponentiate = TRUE -->
<!--                  ) %>% -->
<!--   modify_spanning_header(everything() ~ "Regression for categorical CH VAF≥0.10") -->

<!-- ``` -->
<br>

# VI. Survival - OS
## Univariable regression analysis
Association estimates are reported per 1-SD increase in the body composition metric.

## Univariable - Table S7 (just first section of big table - UVA for BMI)
```{r HR uva cox clinical}
tbl_main_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("age_at_diagnosis_num",
              "sex",
              "stage",
              "ch_status",
              "bmi", "bmi_cat")) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
# tbl_main_surv
```



```{r HR uva cox BC}
tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c(#"imat_cm2", "vat_cm2", "sat_cm2",
              # "muscle_hu", "myosteatosis",
              "v_s_ratio", "visceral_obesity", "tat_cm2"
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

# tbl_sdhr <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("vat_cm2_sdhr", "sat_cm2_sdhr", "imat_cm2_sdhr"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()

# tbl_index <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("smi", "sarcopenia",
#               "imat_cm2_index", "vat_cm2_index", "sat_cm2_index"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
tbl_index_sdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("smi_sdhr",
              "sarcopenia", 
              "muscle_hu_sdhr", "myosteatosis",
              "vat_cm2_index_sdhr", "sat_cm2_index_sdhr",
              "imat_cm2_index_sdhr", "tat_cm2_index_sdhr",
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

# tbl_prop <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("muscle_proportion", "imat_proportion", "vat_proportion", "sat_proportion"
#               )) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()
tbl_propsdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = os_time_from_treatment_months, event = os_event),
  exponentiate = TRUE,
  include = c("muscle_proportion_sdhr", "vat_proportion_sdhr", "sat_proportion_sdhr", "imat_proportion_sdhr"
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

# tbl_cat <- tbl_uvregression(
#   lymphoma_data,
#   method = coxph,
#   y = Surv(time = os_time_from_treatment_months, event = os_event),
#   exponentiate = TRUE,
#   include = c("smi_tertcat", "imat_cm2_index_tertcat", "vat_cm2_index_tertcat", "sat_cm2_index_tertcat",
#               "v_s_ratio_tertcat", "tat_cm2_tertcat",
#               "muscle_proportion_tertcat", "imat_proportion_tertcat", "vat_proportion_tertcat", "sat_proportion_tertcat")) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>%
#   bold_labels() %>% italicize_levels()

```

```{r gt table uva}
gt_tbl <- tbl_stack(list(tbl_main_surv, tbl_index_sdhr_surv, tbl_propsdhr_surv), 
                    group_header = c("Clinical", 
                                     "1-SD normalized Indexed features",
                                     "1-SD normalized Tissue proportion")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```


## Multivariable
## MVA BMI - Table S7
```{r HR mva bmi}
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + bmi,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + bmi_cat,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

### MVA BC - Table 3
```{r}
# tbl_1_surv <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level") %>% 
#   modify_header(label ~ "**MVA Indexed**")
tbl_muscle_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + smi_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") #%>% 
  # modify_header(label ~ "**MVA Indexed**")
tbl_sat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + vat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + imat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_ind_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + smi_sdhr + 
          sat_cm2_index_sdhr +
          vat_cm2_index_sdhr + imat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_muscle_ind_surv, tbl_sat_ind_surv, tbl_vat_ind_surv,
               tbl_imat_ind_surv, tbl_all_ind_surv),
          tab_spanner = c(#"**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metrics**"
                          ))
```
<br>

Table S8 (OS)
```{r}
tbl_muscle_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + muscle_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") #%>% 
  # modify_header(label ~ "**MVA Proportion**")
tbl_sat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + vat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + imat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_prop_surv <-
  coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + 
          sat_proportion_sdhr +
          vat_proportion_sdhr + imat_proportion_sdhr + muscle_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_muscle_prop_surv, tbl_sat_prop_surv, tbl_vat_prop_surv,
               tbl_imat_prop_surv, tbl_all_prop_surv),
          tab_spanner = c(#"**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metric**"
                          ))
```
<br>

<!-- ## Forest plot OS -->
<!-- ```{r forest plot mva HR index} -->
<!-- forest_mva_ind_surv <-  -->
<!--   tbl_muscle_ind_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","SMI")) %>% -->
<!--   mutate(model = "SMI") %>%  -->

<!--   bind_rows(., tbl_sat_ind_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","SAT (index)")) %>% -->
<!--   mutate(model = "SAT")) %>%  -->

<!--   bind_rows(., tbl_vat_ind_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","VAT (index)")) %>% -->
<!--   mutate(model = "VAT")) %>%  -->

<!--   bind_rows(., tbl_imat_ind_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","IMAT (index)")) %>% -->
<!--   mutate(model = "IMAT")) %>%  -->
<!--   separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>%  -->
<!--   mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) %>%  -->
<!--   mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>%  -->
<!--   mutate(model = factor(model, levels = c("SMI",  -->
<!--                                           "VAT", "SAT","IMAT"))) -->

<!-- forest_mva_ind_surv_fig <- -->
<!--   forest_mva_ind_surv %>%  -->
<!--   mutate(Characteristic = fct_relevel(Characteristic, "CH", after = Inf)) %>%  -->
<!--   ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) + -->
<!--   geom_point() +  -->
<!--   geom_errorbarh(height=.1) + -->
<!--   geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + -->
<!--   theme_classic()+ -->
<!--   scale_x_log10()+ -->
<!--   labs(y="", x = "HR (95% CI)")+ -->
<!--   scale_y_discrete( -->
<!--     breaks = c("IMAT", "VAT", "SAT", "SMI", "CH"), -->
<!--     labels = c(expression(IMAT[i]), expression(VAT[i]), expression(SAT[i]), "SMI", "CH") -->
<!--   )+ -->
<!--   theme(text = element_text(size = 15), -->
<!--         axis.title.y = element_blank(), legend.position = "none", -->
<!--         strip.background = element_blank(), -->
<!--         strip.text = element_blank())+ -->
<!--   facet_wrap(. ~ model, ncol = 1, -->
<!--              scales = "free", -->
<!--              strip.position = "right") -->
<!-- # forest_mva_ind_surv -->
<!-- # ggsave("Figures/Figure 1A Forest plot MVA index BC model20260407.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 4, -->
<!-- #        height = 5, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->

<!-- ```{r forest plot mva HR proportion} -->
<!-- forest_mva_prop_surv <-  -->
<!--   tbl_muscle_prop_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","Muscle proportion")) %>% -->
<!--   mutate(model = "SMI") %>%  -->

<!--   bind_rows(., tbl_sat_prop_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","SAT proportion")) %>% -->
<!--   mutate(model = "SAT")) %>%  -->

<!--   bind_rows(., tbl_vat_prop_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","VAT proportion")) %>% -->
<!--   mutate(model = "VAT")) %>%  -->

<!--   bind_rows(., tbl_imat_prop_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","IMAT proportion")) %>% -->
<!--   mutate(model = "IMAT")) %>%  -->
<!--   separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>%  -->
<!--   mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) %>%  -->
<!--   mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>%  -->
<!--   mutate(Characteristic = case_when( -->
<!--     Characteristic == "Muscle"          ~ "SM", -->
<!--     TRUE                                ~ Characteristic -->
<!--   )) %>%  -->
<!--   mutate(model = factor(model, levels = c("SMI",  -->
<!--                                           "VAT", "SAT","IMAT"))) -->

<!-- forest_mva_prop_surv_fig <- -->
<!--   forest_mva_prop_surv %>%  -->
<!--         mutate(Characteristic = fct_relevel(Characteristic, "CH", after = Inf)) %>%  -->
<!--   ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) + -->
<!--   geom_point() +  -->
<!--   geom_errorbarh(height=.1) + -->
<!--   geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + -->
<!--   theme_classic()+ -->
<!--   scale_x_log10()+ -->
<!--   labs(y="", x = "HR (95% CI)")+ -->
<!--   theme(text = element_text(size = 15), -->
<!--         axis.title.y = element_blank(), legend.position = "none", -->
<!--         trip.background = element_blank(), -->
<!--   strip.text = element_blank())+ -->
<!--   facet_wrap(. ~ model, ncol = 1, -->
<!--              scales = "free", -->
<!--              strip.position = "right") -->
<!-- # forest_mva_prop_surv -->
<!-- # ggsave("Figures/Figure 1B Forest plot MVA prop BC model20260407.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 4, -->
<!-- #        height = 5, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- forest_prop_surv <-  -->
<!--   tbl_all_prop_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH","SAT proportion", -->
<!--                                "VAT proportion", -->
<!--                                "IMAT proportion", "Muscle proportion") ) %>%  -->
<!--   mutate(Characteristic = str_remove_all(Characteristic, " proportion")) %>%  -->
<!--   mutate(Characteristic = factor(Characteristic,  -->
<!--                                  levels = c("IMAT", -->
<!--                                             "VAT", -->
<!--                                             "SAT", -->
<!--                                             "Muscle","CH" -->
<!--                                  ))) %>%  -->
<!--   separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>%  -->

<!--   mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) #%>%  -->
<!--   # mutate(name= case_when( -->
<!--   #   Characteristic == "High marrow burden (≥50%)"      ~ "High marrow \nburden (≥50%)", -->
<!--   #   Characteristic == "gr3_cytopenia_-5d"      ~ "Grade ≥ 3 Cytopenia \nat Day -5", -->
<!--   #   Characteristic == "Steroid Use"      ~ "Steroid use", -->
<!--   #   Characteristic == "Number of prior lines of therapy"      ~ "Number of prior \nlines of therapy", -->
<!--   #   Characteristic == "baseline_ferritin_cat"      ~ "Baseline ferritin" -->
<!--   # )) -->

<!-- forest_prop_surv_fig <- -->
<!--   forest_prop_surv %>%  -->
<!--   ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) + -->
<!--   geom_point() +  -->
<!--   geom_errorbarh(height=.1) + -->
<!--   geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + -->
<!--   theme_classic()+ -->
<!--   scale_x_log10()+ -->
<!--     scale_y_discrete( -->
<!--     breaks = c("IMAT", "VAT", "SAT", "Muscle", "CH"), -->
<!--     labels = c("IMAT", "VAT", "SAT", "SM", "CH") -->
<!--   )+ -->
<!--   labs(y="", x = "HR (95% CI)")+ -->
<!--   theme(text = element_text(size = 15), -->
<!--         axis.title.y = element_blank(), legend.position = "none") -->
<!-- # forest_prop_surv_fig -->

<!-- # ggsave("Figures/Figure 1D Forest plot MVA proportion full model20260407.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 6, -->
<!-- #        height = 5, compression = "lzw" -->
<!-- #        ) -->

<!-- forest_ind_surv <- -->
<!--   tbl_all_ind_surv %>% -->
<!--   as_tibble() %>%  -->
<!--   `colnames<-`(str_remove_all(colnames(.), "\\*")) %>%  -->
<!--   filter(Characteristic %in% c("CH", "SMI", "SAT (index)", -->
<!--                                "VAT (index)", -->
<!--                                "IMAT (index)") ) %>%  -->
<!--   mutate(Characteristic = factor(Characteristic,  -->
<!--                                  levels = c("IMAT (index)", -->
<!--                                             "VAT (index)", -->
<!--                                             "SAT (index)", -->
<!--                                             "SMI", "CH" -->
<!--                                  ))) %>%  -->
<!--   separate(`95% CI`, into = c("lower", "upper"), sep = ", ") %>%  -->

<!--   mutate_at(c("HR", "lower", "upper"), ~ as.numeric(.)) -->

<!-- forest_ind_fig_surv <- -->
<!--   forest_ind_surv %>%  -->
<!--   ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) + -->
<!--   geom_point() +  -->
<!--   geom_errorbarh(height=.1) + -->
<!--   geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + -->
<!--   theme_classic()+ -->
<!--   scale_x_log10()+ -->
<!--     scale_y_discrete( -->
<!--     breaks = c("IMAT (index)", "VAT (index)", "SAT (index)", "SMI", "CH"), -->
<!--     labels = c(expression(IMAT[i]), expression(VAT[i]), expression(SAT[i]), "SMI", "CH") -->
<!--   )+ -->
<!--   labs(y="", x = "HR (95% CI)")+ -->
<!--   theme(text = element_text(size = 15), -->
<!--         axis.title.y = element_blank(), legend.position = "none") -->
<!-- forest_ind_fig_surv -->

<!-- # ggsave("Figures/Figure 1C Forest plot MVA indexed full model20260407.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 6, -->
<!-- #        height = 5, compression = "lzw" -->
<!-- #        ) -->

<!-- # forest_surv_fullmva <-  -->
<!-- #   forest_prop_surv %>% -->
<!-- #   mutate(approach = "Proportion") %>%  -->
<!-- #   bind_rows(., forest_ind_surv %>% -->
<!-- #   mutate(approach = "Indexed")) %>%  -->
<!-- #   mutate(Characteristic = str_remove_all(Characteristic, " proportion| \\(index\\)")) %>%  -->
<!-- #   mutate(Characteristic = factor(Characteristic,  -->
<!-- #                                  levels = c("IMAT", -->
<!-- #                                             "VAT", -->
<!-- #                                             "SAT", -->
<!-- #                                             "SMI", "CH" -->
<!-- #                                  ))) %>%  -->
<!-- #   ggplot(aes(y=Characteristic, x=HR, xmin=lower, xmax=upper, color = Characteristic == "CH")) + -->
<!-- #   geom_point() +  -->
<!-- #   geom_errorbarh(height=.1) + -->
<!-- #   geom_vline(xintercept=1, color='black', linetype='dashed', alpha=.5) + -->
<!-- #   theme_classic()+ -->
<!-- #   scale_x_log10()+ -->
<!-- #   labs(y="") %>%  -->
<!-- #   theme(text = element_text(size = 15), -->
<!-- #         axis.title.y = element_blank(), legend.position = "none")+ -->
<!-- #   facet_wrap(. ~ approach, axes = "all", -->
<!-- #              # scales = "free_x", -->
<!-- #              strip.position = "right") -->
<!-- # forest_surv_fullmva -->

<!-- # ggsave("Figures/Figure 1 C-D Forest plot MVA full model20260407.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 6, -->
<!-- #        height = 5, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->

<!-- ```{r patchwork HR forest} -->
<!-- library(patchwork) -->

<!-- # forest_mva_ind_surv <- forest_mva_ind_surv + -->
<!-- #   labs(subtitle = 'Indexed') -->
<!-- # forest_mva_prop_surv <- forest_mva_prop_surv + -->
<!-- #   labs(subtitle = 'Proportion') -->

<!-- (forest_mva_ind_surv_fig + forest_mva_prop_surv_fig) / -->
<!--   (forest_ind_fig_surv + forest_prop_surv_fig) + plot_annotation(tag_levels = 'A')+ -->
<!--   plot_layout(heights = unit(c(2, 1), c('null', 'null'))) -->

<!-- # ggsave("Figures/Figure 1 Forest abcd plot20260721.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 8, -->
<!-- #        height = 6, compression = "lzw" -->
<!-- #        ) -->

<!-- (forest_mva_ind_surv_fig + forest_mva_prop_surv_fig) / -->
<!--   (forest_ind_fig_surv + forest_prop_surv_fig) + plot_annotation(tag_levels = list(c("A", "", "B", "")))+ -->
<!--   plot_layout(heights = unit(c(2, 1), c('null', 'null'))) -->

<!-- # ggsave("Figures/Figure 1 Forest ab plot20260721.tiff", -->
<!-- #        dpi = 600, units = "in", -->
<!-- #        width = 8, -->
<!-- #        height = 6, compression = "lzw" -->
<!-- #        ) -->
<!-- ``` -->
<br>















### Other
```{r}
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + tat_cm2_index_sdhr,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + v_s_ratio,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + visceral_obesity,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sarcopenia,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + myosteatosis,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
             event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + muscle_hu_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```



```{r}
# tbl_3 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           smi + vat_cm2_index + sat_cm2_index + imat_cm2_index,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# tbl_4 <-
#   coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           muscle_proportion + vat_proportion + sat_proportion + imat_proportion,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# 
# 
# tbl_merge(list(tbl_3, tbl_4), tab_spanner = c("**Multivariable \nBody Comp \nIndexed**",
#                                               "**Multivariable \nBody Comp \nProportion**"))
# 
# coxph(Surv(time = lymphoma_data$os_time_from_treatment_months,
#              event = lymphoma_data$os_event) ~ age_at_diagnosis_num +
#           sex + ch_status +
#           v_s_ratio_tertcat,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
```

<!-- Additionally adjusted by BMI -->
<!-- ```{r} -->
<!-- coxph(Surv(time = lymphoma_data$os_time_from_treatment_months, -->
<!--              event = lymphoma_data$os_event) ~ age_at_diagnosis_num + -->
<!--           sex + stage + ch_status + -->
<!--           muscle_proportion + vat_proportion + sat_proportion + imat_proportion +  -->
<!--         bmi, -->
<!--         data = lymphoma_data)  %>% -->
<!--   tbl_regression(exponentiate = TRUE) %>% -->
<!--   bold_p(t = .05) %>% -->
<!--   add_nevent(location = "level") %>% add_n(location = "level") -->

<!-- ``` -->

<!-- ## KM by CH -->
<!-- ```{r KM OS by CH} -->
<!-- ggsurvplot(survfit(Surv(os_time_from_treatment_months, os_event) ~ ch_status, -->
<!--                    data = lymphoma_data), -->
<!--            # title = "PFS Analysis", -->
<!--            font.main = c(20, "bold", "black"), -->
<!--            font.x = c(18, "bold", "black"), -->
<!--            font.y = c(18, "bold", "black"), -->
<!--            font.legend = c(16, "black"), -->
<!--            font.tickslab = c(16, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            xlab = "Time (months)", -->
<!--            legend = "top", -->
<!--            pval = TRUE, -->
<!--            conf.int = FALSE, -->
<!--            # Censor -->
<!--            censor = TRUE -->
<!-- ) %++% guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->

# VII. Survival - PFS
## Univariable regression analysis

## Univariable
```{r HR uva cox clinical pfs}
tbl_main_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = pfs_time_from_treatment_months, event = pfs_event),
  exponentiate = TRUE,
  include = c("age_at_diagnosis_num",
              "sex",
              "stage",
              "ch_status",
              "bmi", "bmi_cat")) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
# tbl_main_surv
```



```{r HR uva cox BC pfs}
tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = pfs_time_from_treatment_months, event = pfs_event),
  exponentiate = TRUE,
  include = c("v_s_ratio", "visceral_obesity", "tat_cm2"
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

tbl_index_sdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = pfs_time_from_treatment_months, event = pfs_event),
  exponentiate = TRUE,
  include = c("smi_sdhr",
              "sarcopenia", 
              "muscle_hu_sdhr", "myosteatosis",
              "vat_cm2_index_sdhr", "sat_cm2_index_sdhr",
              "imat_cm2_index_sdhr", "tat_cm2_index_sdhr",
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()

tbl_propsdhr_surv <- tbl_uvregression(
  lymphoma_data,
  method = coxph,
  y = Surv(time = pfs_time_from_treatment_months, event = pfs_event),
  exponentiate = TRUE,
  include = c("muscle_proportion_sdhr", "vat_proportion_sdhr", "sat_proportion_sdhr", "imat_proportion_sdhr"
              )) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
```

```{r gt table uva pfs}
gt_tbl <- tbl_stack(list(tbl_main_surv, tbl_index_sdhr_surv, tbl_propsdhr_surv), 
                    group_header = c("Clinical", 
                                     "1-SD normalized Indexed features",
                                     "1-SD normalized Tissue proportion")) %>%
  as_gt(#rownames_to_stub = TRUE
  ) %>%
  gt::tab_options(row_group.border.top.color = "black",
                  row_group.border.top.width = 3,
                  row_group.border.bottom.color = "darkgrey",
                  row_group.font.size = 15,
                  row_group.font.weight = "bold",
                  row_group.text_transform = "uppercase",
                  row_group.background.color = "grey")
gt_tbl
```


## Multivariable
## MVA BMI
```{r HR mva bmi pfs}
coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + bmi,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + bmi_cat,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```

### MVA BC - Table 4
```{r mva bc table pfs}
tbl_muscle_ind_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + smi_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") #%>% 
  # modify_header(label ~ "**MVA Indexed**")
tbl_sat_ind_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_ind_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + vat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_ind_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + imat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_ind_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + smi_sdhr + 
          sat_cm2_index_sdhr +
          vat_cm2_index_sdhr + imat_cm2_index_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_muscle_ind_surv, tbl_sat_ind_surv, tbl_vat_ind_surv,
               tbl_imat_ind_surv, tbl_all_ind_surv),
          tab_spanner = c(#"**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metrics**"
                          ))
```
<br>

Table S8 (PFS)
```{r mva bc prop table pfs}
# tbl_1_surv <-
#   coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
#              event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
tbl_muscle_prop_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + muscle_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level") #%>% 
  # modify_header(label ~ "**MVA Proportion**")
tbl_sat_prop_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_vat_prop_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + vat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_imat_prop_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + imat_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
tbl_all_prop_surv <-
  coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + 
          sat_proportion_sdhr +
          vat_proportion_sdhr + imat_proportion_sdhr + muscle_proportion_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")

tbl_merge(list(tbl_muscle_prop_surv, tbl_sat_prop_surv, tbl_vat_prop_surv,
               tbl_imat_prop_surv, tbl_all_prop_surv),
          tab_spanner = c(#"**Multivariable \nClinical only  = 'Reduced model'**",
                          "**Multivariable \nSingle BC model SM**",
                          "**Multivariable \nSingle BC model SAT**",
                          "**Multivariable \nSingle BC model VAT**",
                          "**Multivariable \nSingle BC model IMAT**",
                          "**Multivariable \nFull model 4 metric**"
                          ))
```
<br>



<br>


### Other
```{r other mva pfs}
# coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
#              event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + tat_cm2_index_sdhr,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
#              event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + v_s_ratio,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")
# coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
#              event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
#           sex + stage + ch_status + visceral_obesity,
#         data = lymphoma_data)  %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   bold_p(t = .05) %>%
#   add_nevent(location = "level") %>% add_n(location = "level")

coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + sarcopenia,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + myosteatosis,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
coxph(Surv(time = lymphoma_data$pfs_time_from_treatment_months,
             event = lymphoma_data$pfs_event) ~ age_at_diagnosis_num +
          sex + stage + ch_status + muscle_hu_sdhr,
        data = lymphoma_data)  %>%
  tbl_regression(exponentiate = TRUE) %>%
  bold_p(t = .05) %>%
  add_nevent(location = "level") %>% add_n(location = "level")
```



<!-- ## KM by CH -->
<!-- ```{r KM PFS by CH pfs} -->
<!-- ggsurvplot(survfit(Surv(pfs_time_from_treatment_months, pfs_event) ~ ch_status, -->
<!--                    data = lymphoma_data), -->
<!--            title = "PFS Analysis", -->
<!--            font.main = c(20, "bold", "black"), -->
<!--            font.x = c(18, "bold", "black"), -->
<!--            font.y = c(18, "bold", "black"), -->
<!--            font.legend = c(16, "black"), -->
<!--            font.tickslab = c(16, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            xlab = "Time (months)", -->
<!--            legend = "top", -->
<!--            pval = TRUE, -->
<!--            conf.int = FALSE, -->
<!--            # Censor -->
<!--            censor = TRUE -->
<!-- ) %++% guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->










<br>

<!-- # L-CH -->
<!-- ```{r} -->
<!-- lymphoma_data %>%  -->
<!--   filter(patient_l_ch == "L-CH") %>%  -->
<!--   inner_join(., ch_mutation) %>%  -->
<!--   select(mrn, gene, variant_p, os_event, os_time_from_treatment_months, sex, race, ethnicity_src_desc, myosteatosis, sarcopenia, bmi) -->
<!-- ``` -->



***

sessionInfo available in Readme file

```{r}
sessionInfo() %>% capture.output(file="readme_sessioninfo.txt")
```





